\documentclass[12pt, a4paper]{article}

\usepackage{longtable}
\usepackage{parskip}
\usepackage{amssymb}
\usepackage[top=2cm, bottom=2cm, left=2cm, right=2cm]{geometry}

\begin{document}
\pagenumbering{gobble}
\sffamily
\newgeometry{top=2cm, bottom=2cm, left=0cm, right=0cm}
\renewcommand{\arraystretch}{1.5}
\tiny
\begin{center}
\section*{Sorcerer/Wizard spells from Spell Compendium}
  \subsubsection*{by Gian Marco Cialdi}
  \vspace{15pt}

  \subsubsection*{Level 0}
  \begin{longtable}[H]{ p{8em} p{15em} p{2em} p{5em} p{6em} p{6em} p{10em} p{6em} p{5em} p{2em} }
    \(\blacksquare\) \textbf{Name} & \textbf{Description} & \textbf{School} & \textbf{Comp} & \textbf{Time} & \textbf{Range} & \textbf{T/E/A} & \textbf{Duration} & \textbf{ST} & \textbf{SR}\\
    \endhead
    \(\square\) Electric jolt & Ranged touch attack deals 1d3 electricity damage & Evo & V, S & 1 standard action & Close (25 ft. + 5 ft./2 levels) & Ray & Instantaneous & None & Yes\\
    \(\square\) Sonic snap & Subject takes 1 point of sonic damage and is deafened 1 round & Evo & V, S & 1 standard action & Close (25 ft. + 5 ft./2 levels) & One creature or object & Instantaneous & Will partial & Yes\\
    \(\square\) Caltrops & Creates caltrops in 5-ft-by-5-ft square, + 5-ft square/2 levels beyond 1st (max 5) & Conj & V, S & 1 standard action & Close (25 ft. + 5 ft./2 levels) & See text & 1 round/level & None & No\\
    \(\square\) Amanuensis & Copy nonmagical text & Tra & V, S & 1 standard action & Close (25 ft. + 5 ft./2 levels) & Object or objects with writing & 10 minutes/level & Will negates (object) & Yes (object)\\
    \(\square\) Launch bolt & Launches a crossbow bolt up to 80 ft & Tra & V, S, M & 1 standard action & Touch & One crossbow bolt in your possession & Instantaneous & None & No\\
    \(\square\) Launch item & Hurls Fine item up to Medium range & Tra & S & 1 standard action & Touch & One Fine item in your  & Instantaneous & None & No\\
    \(\square\) Repair minor damage & Repairs 1 point of damage to any construct & Tra & - & - & - & - & - & - & -\\
    \(\square\) Stick & Glues an object weighing 5 pounds or less to another object & Tra & V, S, M & 1 standard action & Touch & Nonmagical, unattended object weighing up to 5 lb. & Instantaneous & Will negates (object) & Yes (object)\\
    \(\square\) Silent portal & Negates sound from door or window & Ill & S & 1 standard action & Close (25 ft. + 5 ft./2 levels) & One portal & 1 minute/level (D) & Will negates (object) & Yes (object)\\
  \end{longtable}

  \subsubsection*{Level 1}
  \begin{longtable}[H]{ p{8em} p{15em} p{2em} p{5em} p{6em} p{6em} p{10em} p{6em} p{5em} p{2em} }
    \(\blacksquare\) \textbf{Name} & \textbf{Description} & \textbf{School} & \textbf{Comp} & \textbf{Time} & \textbf{Range} & \textbf{T/E/A} & \textbf{Duration} & \textbf{ST} & \textbf{SR}\\
    \endhead
    \(\square\) Dispel ward & As dispel magic, but affects only wards & Abj & V, S & 1 standard action & Medium (100 ft. + 10 ft./level) & One warded object or area & Instantaneous & None & No\\
    \(\square\) Ectoplasmic armor & Gain armor bonus against incorporeal touch attacks & Abj & V & 1 standard action & Touch & Creature touched & 1 hour/level (D) & Will negates (harmless) & No\\
    \(\square\) Ironguts & Subject gains +5 bonus on saving throws against poison & Abj & V, S, M & 1 standard action & Touch & Creature touched & 10 minutes/level & Will negates & Yes\\
    \(\square\) Nightshield & You gain resistance bonus on saves, and spell absorbs magic missile damage & Abj & V, S & 1 standard action & Personal & You & 1 minute/level (D) & - & -\\
    \(\square\) Resist planar alignment & Subject can resist penalties for being of an opposed alignment on an aligned Outer Plane & Abj & V, S, DF & 1 standard action & Touch & Creature touched & 10 minutes/level & Fortitude negates (harmless) & Yes (harmless)\\
    \(\square\) Blood wind & Subject uses natural weapons at range & Evo & V, S & 1 swift action & Close (25 ft. + 5 ft./2 caster levels) & A single creature with Intelligence 4 or higher & 1 round & Will negates (harmless) & Yes (harmless)\\
    \(\square\) Guiding light & +2 on ranged attacks against creatures in illuminated area & Evo & V, S & 1 standard action & Long (400 ft. + 40 ft./level) & - & 1 minute/level (D) & None & Yes\\
    \(\square\) Ice dagger & Grenadelike weapon deals subject 1d4/level cold damage, plus area damage & Evo & V, S, M & 1 standard action & Close (25 ft. + 5 ft./2 levels) & Dagger of ice & Instantaneous & None & Yes\\
    \(\square\) Light of lunia & You radiate silvery light, which you can expend as 2 bolts that deal 1d6 damage & Evo & V, S & 1 standard action & Medium (100 ft. + 10 ft./level) & nd  & 10 minutes/level (D) or until discharged; see text & None & Yes; see text\\
    \(\square\) Luminous gaze & Your eyes emit light, dazzle creatures & Evo & V, S & 1 standard action & Personal & You & 1 round/level & - & -\\
    \(\square\) Persistent blade & Blade of force attacks subject, automatically ﬂanks & Evo & V, S, F & 1 standard action & Close (25 ft. + 5 ft./2 levels) & One dagger made of force & 1 round/level & None & Yes\\
    \(\square\) Ray of flame & Ray deals 1d6/2 levels ﬁre damage, ignites subject & Evo & V, S, F & 1 standard action & Close (25 ft. + 5 ft./2 levels) & Ray & Instantaneous & See text & Yes\\
    \(\square\) Sonic blast & Subject takes 1d4/2 levels sonic damage plus deafness & Evo & V, S & 1 standard action & Close (25 ft. + 5 ft./2 levels) & One creature & Instantaneous & Will partial & Yes\\
    \(\square\) Thunderhead & Small lightning bolts deal 1 damage/round & Evo & V, S, M & 1 standard action & Close (25 ft. + 5 ft./2 levels) & One creature & 1 round/level & Reﬂex negates; see text & Yes\\
    \(\square\) Benign transposition & Two willing subjects switch places & Conj & V & 1 standard action & Medium (100 ft. + 10 ft./level) & - & Instantaneous & None & No\\
    \(\square\) Blades of fire & Your melee weapons deal +1d8 ﬁre damage for 1 round & Conj & V & 1 swift action & Touch & - & 1 round & None & No\\
    \(\square\) Buzzing bee & Bee gives subject –10 penalty on Move Silently and hinders Concentration checks & Conj & V, S, M & 1 standard action & Medium (100 ft. + 10 ft./level) & One creature & 1 minute/level (D) & None & No\\
    \(\square\) Corrosive grasp & 1 touch/level deals 1d8 acid damage & Conj & V, S & 1 standard action & Touch & - & Instantaneous & None & Yes\\
    \(\square\) Deep breath & Your lungs are ﬁlled with air & Conj & V & 1 immediate action & Personal & You & 1 round/level & - & -\\
    \(\square\) Hail of stone & Stones deal 1d4 points of damage/level to creatures in the area (max 5d4) & Conj & V, S, M & 1 round & Medium (100 ft. + 10 ft./level) & Cylinder (5-ft. radius, 40 ft. high) & Instantaneous & None & No\\
    \(\square\) Orb of acid, lesser & Ranged touch attack deals 1d8 acid damage + 1d8/2 levels beyond 1st (max 5d8) & Conj & V, S & 1 standard action & Close (25 ft. + 5 ft./2 levels) & One orb of acid & Instantaneous & None & No\\
    \(\square\) Orb of cold, lesser & Ranged touch attack deals 1d8 cold damage + 1d8/2 levels beyond 1st (max 5d8) & Conj & - & - & - & One orb of cold & - & - & -\\
    \(\square\) Orb of electricity, lesser & Ranged touch attack deals 1d8 electricity damage + 1d8/2 levels beyond 1st (max 5d8) & Conj & - & - & - & One orb of electricity & - & - & -\\
    \(\square\) Orb of fire, lesser & Ranged touch attack deals 1d8 ﬁre damage + 1d8/2 levels beyond 1st (max 5d8) & Conj & - & - & - & One orb of ﬁre & - & - & -\\
    \(\square\) Orb of sound, lesser & Ranged touch attack deals 1d6 sonic damage + 1d6/2 levels beyond 1st (max 5d6) & Conj & - & - & - & One orb of sonic energy & - & - & -\\
    \(\square\) Summon undead i & Summons undead to ﬁght for you & Conj & V, S, F/DF & 1 round & Close (25 ft. + 5 ft./2 levels) & One summoned creature & 1 round/level & None & No\\
    \(\square\) Wall of smoke & Wall of black smoke obscures vision and nauseates those who pass through & Conj & V, S & 1 standard action & Close (25 ft. + 5 ft./2 levels) & A straight wall whose area is up to one 10-ft. square/level (S) & 1 round/level & Fortitude partial; see text & No\\
    \(\square\) Accelerated movement & Balance, Climb, or Move Silently at normal speed with no penalty on skill check & Tra & S, M & 1 swift action & Personal & You & 1 round/level (D) & - & -\\
    \(\square\) Babau slime & Secrete a body-covering acid that damages attacking foes & Tra & V, S, M/DF & 1 standard action & Touch & Creature touched & 1 minute/level & Fortitude negates (harmless) & Yes (harmless)\\
    \(\square\) Breath flare & Your breath weapon dazzles subjects & Tra & S & 1 swift action & Personal & Your breath weapon & 1 round & - & -\\
    \(\square\) Cheat & Caster rerolls when determining the success of a game of chance & Tra & V, S, F & 1 standard action & Personal & You & 1 minute/level or until discharged & Will negates; see text & No\\
    \(\square\) Cutting hand & Your hand gains a +2 enhancement bonus and deals 1d6 damage & Tra & V, S & 1 standard action & Personal & Your hand & 1 round/level (D) & - & -\\
    \(\square\) Ebon eyes & Subject can see through magical darkness & Tra & V, S, M & 1 standard action & Touch & Creature touched & 10 minutes/level & None & Yes (harmless)\\
    \(\square\) Expeditious retreat, swift & Your speed increases by 30 ft for 1 round & Tra & V & 1 swift action & - & - & 1 round & - & -\\
    \(\square\) Fist of stone & Gain +6 Str and natural slam attack & Tra & V, S, M & 1 standard action & Personal & You & 1 minute & - & -\\
    \(\square\) Horrible taste & Touched creature or object nauseates biting or swallowing foes & Tra & V, S, M & 1 standard action & Touch & Creature or object touched & 10 minutes/level & Fortitude negates; see text & No\\
    \(\square\) Low-light vision & See twice as far as a human in poor illumination & Tra & V, M & 1 standard action & Touch & Creature touched & 1 hour/level & Will negates (harmless) & Yes (harmless)\\
    \(\square\) Mage hand, greater & As mage hand, but medium range and up to 40 lb & Tra & V, S & 1 standard action & Medium (100 ft. + 10 ft./level) & One object or creature weighing up to 40 lb. & Concentration & Will negates & Yes\\
    \(\square\) Nerveskitter & Subject gains +5 bonus on initiative checks & Tra & V, S & 1 immediate action & Close (25 ft. + 5 ft./2 levels) & One creature & 1 round & None (harmless) & Yes\\
    \(\square\) Portal beacon & You grant others knowledge of a magic portal’s location & Tra & V, S & 1 standard action & Close (25 ft. + 5 ft./2 levels) & One interplanar gate or portal & 1 hour/level & None & No\\
    \(\square\) Raging flame & Fires burn twice as hot, half as long & Tra & V, S & 1 standard action & Medium (100 ft. + 10 ft./level) & 30-ft.-radius spread & 1 minute & None & No\\
    \(\square\) Ray of clumsiness & Victim takes 1d6 Dexterity penalty +1/2 levels & Tra & V, S & 1 standard action & Close (25 ft. + 5 ft./2 levels) & Ray & 1 minute/level & None & Yes\\
    \(\square\) Remove scent & Hides touched creature’s scent & Tra & V, S, M & 1 standard action & Touch & Creature touched & 10 minutes/level & Will negates & Yes\\
    \(\square\) Repair light damage & Repairs 1d8 damage +1/level (max +5) to any construct & Tra & V, S & 1 standard action & Touch & Construct touched & Instantaneous & None & No\\
    \(\square\) Scatterspray & Group of small objects ﬂies apart in a burst & Tra & V, S & 1 standard action & Close (25 ft. + 5 ft./2 levels) & - & Instantaneous & See text & No\\
    \(\square\) Shieldbearer & Shield ﬂoats near subject to offer protection & Tra & V, S & 1 standard action & Touch & Shield touched & 1 round/level & None & No\\
    \(\square\) Slide & Move subject 5 feet & Tra & V & 1 standard action & Close (25 ft. + 5 ft./2 levels) & One creature & Instantaneous & Will negates & Yes\\
    \(\square\) Slow burn & Fires burn twice as long & Tra & V, S, M/DF & 1 standard action & Medium (100 ft. + 10 ft./level) & 30-ft.-radius spread & 1 minute & None & No\\
    \(\square\) Spell flower & Hold the charge on one touch spell per forelimb & Tra & V, S & 1 standard action & Personal & You & 1 round/level & - & -\\
    \(\square\) Weapon shift & Touched weapon changes form & Tra & V, S, M & 1 standard action & Touch & One melee weapon of up to 15 lb. & 1 minute/level & Fortitude negates (object) & Yes (object)\\
    \(\square\) Wings of the sea & +30 ft to subject’s swim speed & Tra & S, M & 1 standard action & Touch & Creature touched & 1 minute/level & Fortitude negates (harmless) & Yes (harmless)\\
    \(\square\) Appraising touch & Gain +10 bonus on Appraise checks & Div & V, S & 1 standard action & Personal & You & 1 hour/level & - & -\\
    \(\square\) Arrow mind & You threaten nearby squares with your bow and ﬁre without provoking attacks of opportunity & Div & V, S, M & 1 immediate action & Personal & You & 1 minute/level (D) & - & -\\
    \(\square\) Critical strike & For 1 round you gain +1d6 damage, doubled threat range, and +4 on attack rolls to conﬁrm critical threats & Div & V & 1 swift action & Personal & You & 1 round & - & -\\
    \(\square\) Golem strike & You can sneak attack constructs for 1 round & Div & V & 1 swift action & Personal & You & 1 round & - & -\\
    \(\square\) Guided shot & You ignore distance, cover, concealment penalties with your ranged attacks for 1 round & Div & V & 1 swift action & Personal & You & 1 round & - & -\\
    \(\square\) Insightful feint & Gain +10 on your next Bluff check to feint in combat & Div & V & 1 swift action & Personal & You & 1 round & - & -\\
    \(\square\) Instant locksmith & Make Disable Device or Open Lock check at +2 as free action & Div & V, S & 1 swift action & Personal & You & 1 round & - & -\\
    \(\square\) Instant search & Make Search check at +2 as free action & Div & V, S & 1 swift action & Personal & You & 1 round & - & -\\
    \(\square\) Master’s touch & You gain proﬁciency in a weapon or shield touched for 1 minute/level & Div & V, F & 1 swift action & Personal & You & 1 minute/level (D) & - & -\\
    \(\square\) Sniper’s shot & No range limit on next ranged sneak attack & Div & V, S & 1 swift action & Personal & You & 1 round & - & -\\
    \(\square\) Spontaneous search & Instantly Search area as if having taken 10 & Div & V, S, M & 1 round & Touch & Creature touched & 1 round & Will negates (harmless) & Yes (harmless)\\
    \(\square\) Targeting ray & You and allies are +1 to hit/3 levels against subject & Div & V, S, F & 1 standard action & Medium (100 ft. + 10 ft./level) & Ray & 1 round/level & None & No\\
    \(\square\) Distract & Subjects take –4 on Concentration, Listen, Search, and Spot & Ench & S & 1 standard action & Medium (100 ft. + 10 ft./level) & - & 1 round/level & Will negates & Yes\\
    \(\square\) Distract assailant & One creature is ﬂat-footed for 1 round & Ench & V, S, M & 1 swift action & Close (25 ft. + 5 ft./2 levels) & One creature & 1 round & Will negates & Yes\\
    \(\square\) Incite & Subjects can’t ready actions or delay & Ench & V, S & 1 swift action & Close (25 ft. + 5 ft./2 levels) & Creatures in a 10-ft. burst & 1 minute/level & Will negates & Yes\\
    \(\square\) Inhibit & Subject delays until next round & Ench & V, S & 1 standard action & Medium (100 ft. + 10 ft./level) & One creature & InstantaneousSa ving Throw: Will negates & - & Yes\\
    \(\square\) Shock and awe & Flat-footed creatures get –10 on initiative & Ench & V, S & 1 swift action & Close (25 ft. + 5 ft./2 levels) & - & 1 round & None & Yes\\
    \(\square\) Dead end & Removes spoor of one creature/level & Ill & V, S, M & 1 standard action & Touch & - & 10 minutes/level (D) & Will negates (harmless) or Will disbelief (if interacted with); see text & Yes\\
    \(\square\) Net of shadows & Ordinary shadows that provide concealment to all in the area & Ill & V, S & 1 standard action & Close (25 ft. + 5 ft./2 levels) & - & 1d6 rounds & Will negates & Yes\\
    \(\square\) Serene visage & Gain insight bonus on Bluff checks equal to half your level & Ill & V, S & 1 standard action & Personal & You & 1 minute/level & - & -\\
    \(\square\) Backbiter & Weapon strikes wielder & Nec & V, S, F & 1 standard action & Close (25 ft. + 5 ft./2 levels) & One weapon & 1 round/level or until discharged & Will negates; see text & Yes (object)\\
    \(\square\) Spirit worm & Subject takes 1 point Con damage every round for 1 round/level & Nec & V, S, M & 1 standard action & Touch & Living creature touched & 1 round/level, up to 5 rounds; see text & Fortitude negates; see text & Yes\\
    \(\square\) Familiar pocket & Garment or container becomes extradimensional safe haven for your familiar & Uni & V, S, M & 1 standard action & Touch & One container or garment with a pocket touched & 1 hour/level (D) & None & No\\
  \end{longtable}

  \subsubsection*{Level 2}
  \begin{longtable}[H]{ p{8em} p{15em} p{2em} p{5em} p{6em} p{6em} p{10em} p{6em} p{5em} p{2em} }
    \(\blacksquare\) \textbf{Name} & \textbf{Description} & \textbf{School} & \textbf{Comp} & \textbf{Time} & \textbf{Range} & \textbf{T/E/A} & \textbf{Duration} & \textbf{ST} & \textbf{SR}\\
    \endhead
    \(\square\) Aiming at the target & +10 bonus on Concentration checks for previously cast spell & Abj & S & 1 immediate action & Personal & You & Concentration, up to 20  & - & -\\
    \(\square\) Alarm, greater & As alarm, and it works on coexistent planes & Abj & V, S, F & - & - & - & 4 hours/level (D) & - & -\\
    \(\square\) Daggerspell stance & You gain +2 insight bonus on attack rolls and damage rolls if you make a full attack, SR 5 + caster level if you ﬁght defensively, and DR 5/magic if you use the total defense action & Abj & V, F & 1 swift action & Personal & You & 1 round/level (D) & - & -\\
    \(\square\) Dissonant chant & Concentration checks more difﬁcult within area of spell & Abj & V, S & 1 standard action & Close (25 ft. + 5 ft./2 levels) & 100-foot-radius emanation & 1 round/level (D) & None; see text & Yes\\
    \(\square\) Distracting ray & Ray forces spellcaster to make Concentration check & Abj & V, S & 1 standard action & Close (25 ft. + 5 ft./2 levels) & Ray & Instantaneous & None & No\\
    \(\square\) Earth lock & Constricts tunnel, preventing access & Abj & V, S, M & 1 standard action & Close (25 ft. + 5 ft./2 levels) & One 1-foot length of tunnel with a diameter of up to 10 feet & Permanent & None & No\\
    \(\square\) Ectoplasmic feedback & Incorporeal attackers take 1d6 damage + 1/level & Abj & V, S & 1 standard action & Personal & You & 1 minute/level (D) & None & See text\\
    \(\square\) Portal alarm & You are alerted when a creature passes through a warded portal & Abj & V, S, M & 1 standard action & Close (25 ft. + 5 ft./2 levels) & One interplanar gate or portal & 2 hours/level (D) & None & No\\
    \(\square\) Scintillating scales & Your natural armor bonus turns into a deﬂection bonus & Abj & V & 1 standard action & Personal & You & 1 minute/level & - & -\\
    \(\square\) Battering ram & Deals 1d6 damage plus bull rush & Evo & V, S, F & 1 standard action & Close (25 ft. + 5 ft./2 levels) & One object or creature & Instantaneous & None & Yes\\
    \(\square\) Blast of force & Attack deals 1d6 damage/2 levels (max 5d6) & Evo & V, S & 1 standard action & Medium (100 ft. + 10 ft./level) & Ray & Instantaneous & Fortitude partial & Yes\\
    \(\square\) Burning sword & Weapon gains ﬂaming burst special ability & Evo & V, S & 1 standard action & Touch & Weapon touched & 1 minute/level (D) & None & No\\
    \(\square\) Combust & Subject takes 1d8/level ﬁre damage and might catch ﬁre & Evo & V, S, M & 1 standard action & Touch & Touched creature or combustible object that weighs no more than 25 lb./level & Instantaneous; see text & Reﬂex partial & Yes\\
    \(\square\) Electric loop & Deals 1d6/2 levels electricity damage plus stunning to a single creature & Evo & V, S, M & 1 standard action & Close (25 ft. + 5 ft./2 levels) & - & Instantaneous & Reﬂex half; see text & Yes\\
    \(\square\) Ethereal chamber & You entrap an ethereal subject in a chamber of force & Evo & V, S, M & 1 standard action & Close (25 ft. +  & - & - & - & -\\
    \(\square\) Fireburst & Creatures within 10 feet take 1d8/level ﬁre damage & Evo & V, S, M & 1 standard action & 10 ft. & Burst of ﬁre extending 10 ft. from you & Instantaneous & Reﬂex half & Yes\\
    \(\square\) Flame dagger & Beam of ﬁre deals 1d4 damage +1/level & Evo & V, S, M & 1 standard action & 0 ft. & A daggerlike beam & 1 minute/level (D) & None & Yes\\
    \(\square\) Frost breath & Icy breath deals 1d4 damage/2 levels & Evo & V, S, M & 1 standard action & 30 ft. & Cone-shaped burst & Instantaneous & Reﬂex half & Yes\\
    \(\square\) Light of mercuria & You radiate golden light, which you can expend as 2 bolts that deal 1d6 damage, 2d6 against undead and evil outsiders & Evo & - & - & - & - & - & - & -\\
    \(\square\) Rainbow beam & Ray dazzles and deals 1d12 damage/3 levels of random type & Evo & V, S, F & 1 standard action & Close (25 ft. + 5 ft./2 levels) & Ray & Instantaneous & None & Yes\\
    \(\square\) Ray of ice & Ray deals 1d6 cold damage/2 levels & Evo & V, S, M & 1 standard action & Close (25 ft. + 5 ft./2 levels) & Ray & Instantaneous & See text & Yes\\
    \(\square\) Scorch & Jet of ﬂame deals 1d8/2 levels (max 5d8) & Evo & V, S, F & 1 standard action & 30 ft. & 30-ft. line & Instantaneous & Reﬂex half & Yes\\
    \(\square\) Slapping hand & Hand makes creature provoke attacks of opportunity & Evo & V, S, F & 1 standard action & Medium (100 ft. + 10 ft./level) & One Tiny hand & Instantaneous & None; see text & Yes\\
    \(\square\) Snowball swarm & Snowballs deal 2d6 points of cold damage in 10-ft burst & Evo & V, S, M & 1 standard action & Medium (100 ft. + 10 ft./level) & 10-ft.-radius burst & Instantaneous & Reﬂex half & Yes\\
    \(\square\) Baleful transposition & Two subjects switch places & Conj & V & 1 standard action & Medium (100 ft. + 10 ft./level) & - & Instantaneous & Will negates & Yes\\
    \(\square\) Cloud of bewilderment & Generates a nauseating 10-ft cube & Conj & V, S, M & 1 standard action & Close (25 ft. + 5 ft./2 levels) & 10-ft. cube & 1 round/level & Fortitude negates; see text & No\\
    \(\square\) Create magic tattoo & Subject receives a magic tattoo with various effects & Conj & V, S, M, F & 10 minutes & Touch & Creature touched & 24 hours & None & Yes (harmless)\\
    \(\square\) Ice knife & Magical shard of ice deals 2d8 cold damage plus 2 Dex damage, or deals 1d8 cold damage in 10-ft-radius burst & Conj & S, M & 1 standard action & Long (400 ft. + 40 ft./level) & One icy missile & Instantaneous & Fortitude partial or Reﬂex half; see text & Yes\\
    \(\square\) Malevolent miasma & Cloud of fog deals 1d4 nonlethal damage/level & Conj & V, S, F & 1 standard action & Close (25 ft. + 5 ft./2 levels) & 15-ft.-radius burst & Instantaneous & Fortitude negates & No\\
    \(\square\) Summon undead ii & Summons undead to ﬁght for you & Conj & - & - & - & One or more summoned  & - & - & -\\
    \(\square\) Augment familiar & Your familiar becomes more powerful & Tra & V, S & 1 standard action & Close (25 ft. + 5 ft./2 levels) & Your familiar & Concentration + 1 round/level & Fortitude negates (harmless) & Yes (harmless)\\
    \(\square\) Balor nimbus & Your ﬂaming body damages foes in grapple & Tra & V, S, M/DF & 1 standard action & Personal & You & 1 round/level & None & No\\
    \(\square\) Belker claws & Touch attack deals 2d12 damage and lingers +1 round/3 levels & Tra & V, S, M & 1 standard action & Touch & Living creature & Instantaneous & None & Yes\\
    \(\square\) Body of the sun & Your body emanates ﬁre, dealing 1d4 ﬁre damage/2 levels & Tra & V, S, DF & 1 standard action & 5 ft. & 5-ft.-radius emanation centered on you & 1 round/level & Reﬂex half & Yes\\
    \(\square\) Bristle & Armor spikes attack with wearer & Tra & V, S & 1 standard action & Touch & Suit of armor touched & 1 minute/level (D) & None & No\\
    \(\square\) Earthbind & Subject creature can’t ﬂy & Tra & V, S & 1 standard action & Medium (100 ft. + 10 ft./level) & One creature & 1 minute/level (D) & Fortitude negates & Yes\\
    \(\square\) Earthen grasp & Arm made of earth and soil grapples foes & Tra & V, S, M & 1 standard action & Close (25 ft. + 5 ft./2 levels) & Animated earthen arm & 2 rounds/level & None & Yes\\
    \(\square\) Extend tentacles & +5 ft to reach of tentacle attack & Tra & V & 1 standard action & Personal & You & 1 round/level & - & -\\
    \(\square\) Fearsome grapple & You grow tentacles that help you grapple & Tra & V & 1 immediate action & Personal & You & 1 round/level & - & -\\
    \(\square\) Fins to feet & Transforms tails and fins into legs and feet & Tra & V, S & 1 standard action & Touch & Willing creature touched & 1 hour/level & Fortitude negates (harmless) & Yes (harmless)\\
    \(\square\) Fuse arms & Multiple arms/tentacles become one pair of stronger limbs & Tra & V, S & 1 standard action & Touch & Creature with at least two arms or tentacles touched & 10 minutes/level & Fortitude negates (harmless) & Yes (harmless)\\
    \(\square\) Ghost touch armor & Armor works normally against incorporeal attacks & Tra & V, S, M & 1 standard action & Touch & Armor of creature touched & 1 minute/level & Will negates (harmless) & Yes (harmless)\\
    \(\square\) Heroics & Fighter gains one ﬁghter bonus feat & Tra & V, S, M & 1 standard action & Touch & Creature touched & 10 minutes/level & None & Yes\\
    \(\square\) Hurl & Thrown weapon returns to thrower & Tra & V, S & 1 standard action & Touch & Weapon touched & 1 minute/level & None & No\\
    \(\square\) Infernal wound & Weapon deals persistent, bleeding wounds & Tra & V, S & 1 standard action & Touch & Weapon touched & 1 round/level & None & No\\
    \(\square\) Ironthunder horn & Intense vibrations trip those in area & Tra & V, S & 1 standard action & 30 ft. & Cone-shaped burst & Instantaneous & Reﬂex negates & Yes\\
    \(\square\) Lively step & You and allies gain +10 increase to speed & Tra & V, S, F & 1 standard action & 30 ft. & 30-ft.-radius emanation centered on you & Up to 12 hours & Will negates (harmless) & Yes (harmless)\\
    \(\square\) Mountain stance & Subject becomes hard to move & Tra & V, S & 1 standard action & Touch & One creature & 1 minute/level & Will negates (harmless) & No\\
    \(\square\) Quick potion & Creates a potion that must be used within 1 hour/level & Tra & V, S & 1 minute & Touch & Flask of water touched & 1 hour/level & Will negates (object) & Yes (object)\\
    \(\square\) Razorfangs & Your bite or claw attack threatens a critical hit on a 19 or 20 & Tra & V & 1 standard action & Personal & You & 1 round/level & - & -\\
    \(\square\) Repair moderate damage & Repairs 2d8 damage +1/level (max +10) to any construct & Tra & - & - & - & - & - & - & -\\
    \(\square\) Scale weakening & Subject’s natural armor weakens & Tra & V, S, M & 1 standard action & Close (25 ft. + 5 ft./2 levels) & Ray & 1 minute/level (D) & None & Yes\\
    \(\square\) Slide, greater & Move subject 20 feet & Tra & - & - & Medium (100 ft. + 10 ft./level) & - & - & - & -\\
    \(\square\) Snake’s swiftness & Subject immediately makes one attack & Tra & V, S, M/DF & 1 standard action & Close (25 ft. + 5 ft./2 levels) & One allied creature & Instantaneous & Will negates (harmless) & Yes (harmless)\\
    \(\square\) Sonic weapon & Weapon touched deals +1d6 sonic damage with each hit & Tra & V & 1 standard action & Touch & Weapon touched & 1 minute/level (D) & - & -\\
    \(\square\) Speak to allies & Subjects can converse at distance without moving lips & Tra & - & - & - & - & - & - & -\\
    \(\square\) Stone bones & Corporeal undead gains +3 natural armor bonus & Tra & V, S, F & 1 standard action & Touch & Corporeal undead creature touched & 10 minutes/level & Will negates (harmless) & Yes (harmless)\\
    \(\square\) Surefooted stride & You can move over rubble as easily as you can over open ground & Tra & V, S & 1 standard action & Personal & You & 1 minute/level & None & No\\
    \(\square\) Swim & Subject gains swim speed, +8 bonus on Swim checks & Tra & V, S, M & 1 round & Medium (100 ft. + 10 ft./level) & One creature & 10 minutes/level (D) & None & Yes (harmless)\\
    \(\square\) Whirling blade & Hurled slashing weapon magically attacks all foes in 60-ft line & Tra & V, S, F & 1 standard action & 60 ft. & 60-ft. line & Instantaneous & None & No\\
    \(\square\) Wings of air & Subject’s ﬂight maneuverability improves by one step & Tra & V & 1 standard action & Touch & Winged creature touched & 1 minute/level & None (harmless) & No (harmless)\\
    \(\square\) Wraithstrike & Your melee attacks strike as touch attacks for 1 round & Tra & V, S & 1 swift action & Personal & You & 1 round & - & -\\
    \(\square\) Balancing lorecall & You gain a +4 bonus on Balance checks and can balance on difﬁcult surfaces if you have 5 or more ranks in Balance & Div & V, S, M/DF & 1 standard action & Personal & You & 1 minute/level (D) & - & -\\
    \(\square\) Chain of eyes & See through other creatures’ eyes & Div & V, S & 1 standard action & Touch & Living creature touched & 1 hour/level & Will negates & Yes\\
    \(\square\) Discern shapechanger & Penetrates disguises and identiﬁes shapechanging creatures & Div & V, S, M & 1 round & Personal & You & 1 round/level & - & -\\
    \(\square\) Marked object & You gain bonus to track a speciﬁc being & Div & V, S, F & 1 minute & Personal & You & 24 hours/level & - & -\\
    \(\square\) Entice gift & Subject gives caster what it’s holding & Ench & V, S & 1 standard action & Close (25 ft. + 5 ft./2 levels) & One creature & 1 round & Will negates & Yes\\
    \(\square\) Mechanus mind & Reformat subject’s mind to be coldly calculating & Ench & V, S & 1 standard action & Touch & Creature touched & 1 minute/level & Fortitude negates (harmless) & Yes (harmless)\\
    \(\square\) Mindless rage & Subject compelled to attack you physically for 1 round/level & Ench & V, S, F & 1 standard action & Medium (100 ft. + 10 ft./level) & One creature & 1 round/level & Will negates & Yes\\
    \(\square\) Ray of stupidity & Victim takes 1d4+1 Intelligence damage & Ench & V, S, M & 1 standard action & Close (25 ft. + 5 ft./2 levels) & Ray & Instantaneous & None & Yes\\
    \(\square\) Rebuke & Subject is dazed 1 round, then shaken & Ench & V, S, F & 1 standard action & Close (25 ft. + 5 ft./2 levels) & One living creature & 1 round/level & Will negates & Yes\\
    \(\square\) Sting ray & Subject of ray can take only standard or move action, has –2 AC, and must make Concentration checks to cast spells & Ench & V, S, M & 1 standard action & Close (25 ft. + 5 ft./2 levels) & Ray & 1 round/level & Will partial & Yes\\
    \(\square\) Bladeweave & Your melee attack dazes your opponent & Ill & V & 1 swift action & Personal & You & 1 round/level (D) & See text & See text\\
    \(\square\) Claws of darkness & Claws deal 1d8 cold damage and have reach & Ill & V, S & 1 standard action & Personal & You & 1 round/level (D) & Fortitude partial & Yes; see text\\
    \(\square\) Cloak pool & Hide a color pool on the Astral Plane from view & Ill & V, S & 1 standard action & Close (25 ft. + 5 ft./2 levels) & One color pool & 1 hour/level (D) & Will negates (harmless, object) & No\\
    \(\square\) Dark way & Creates temporary unbreakable bridge supporting up to 200 lb & Ill & V, S, DF & 1 standard action & Close (25 ft. + 5 ft./2 levels) & One bridge of force 5 ft. wide, 1 in. thick, and up to 20 ft./level long & 1 round/level & None & Yes\\
    \(\square\) Delusions of grandeur & Subject thinks it is better than it is & Ill & V & 1 standard action & Medium (100 ft. + 10 ft./level) & One creature & 10 minutes/level & Will negates & Yes\\
    \(\square\) Discolor pool & Change the color of a color pool on the Astral Plane & Ill & V, S, M & 1 standard action & Close (25 ft. + 5 ft./2 levels) & One color pool & 1 hour/level (D) & Will disbelief (if interacted with) & No\\
    \(\square\) Disguise undead & Change appearance of one corporeal undead & Ill & V, S, F & 1 standard action & TouchTa rget: 1 corporeal undead & - & 24 hours & None & -\\
    \(\square\) Phantasmal assailants & Nightmare creatures strike subject for 8 Wis damage, 8 Dex damage & Ill & V, S & 1 standard action & Close (25 ft. + 5 ft./2 levels) & One living creature & Instantaneous & Will disbelief (if interacted with), then Fortitude half; see text & Yes\\
    \(\square\) Phantom foe & Subject is always ﬂanked by one creature & Ill & V, S, F & 1 standard action & Touch & Creature touched & 1 round/level & Will disbelief & No\\
    \(\square\) Reflective disguise & Viewers see you as their own species and gender & Ill & V, S & 1 standard action & Personal & You & 10 minutes/level & - & -\\
    \(\square\) Shadow mask & Grants +4 on saves against light spells, protection from gaze attacks & Ill & V, S, M & 1 standard action & Personal & You & 10 minutes/level (D) & - & -\\
    \(\square\) Shadow radiance & Area ﬁlled with intense light that grows brighter & Ill & V, S, M & 1 standard action & Medium (100 ft. + 10 ft./level) & 20-ft.-radius burst centered on a point in space & 1 round/level & Will disbelief (if interacted with) & Yes\\
    \(\square\) Shadow spray & Deals 4 points of Str damage and dazes & Ill & V, S, M & 1 standard action & Medium (100 ft. + 10 ft./level) & 5-ft.-radius burst & 1 round/level & Fortitude negates & Yes\\
    \(\square\) Wall of gloom & Shadow barrier obscures vision & Ill & V, S, M & 1 standard action & Medium (100 ft. + 10 ft./level) & A straight wall whose area is up to one 10-ft. square/level & Concentration + 1 round/level & None & No\\
    \(\square\) Bonefiddle & Spectral fiddle bow deals 3d6 damage/round & Nec & V, S, F & 1 standard action & Close (25 ft. + 5 ft./2 levels) & One creature with a skeleton or exoskeleton & Concentration, up to 1 round/level & Fortitude negates & Yes\\
    \(\square\) Curse of impending blades & Subject takes –2 penalty to AC & Nec & V, S, M/DF & 1 standard action & Medium (100 ft. + 10 ft./level) & One creature & 1 minute/level & None & Yes\\
    \(\square\) Death armor & Black aura damages creatures attacking you & Nec & V, S, M, F & 1 standard action & Personal & You & 1 round/level & - & -\\
    \(\square\) Desiccating bubble & Globe of air damages by evaporating moisture from subject & Nec & S, M/DF & 1 standard action & Medium (100 ft. + 10 ft./level) & 3-ft.-radius sphere of air & 1 round/level & Reﬂex negates & Yes\\
    \(\square\) Ghoul glyph & Glyph wards area, paralyzes victims & Nec & V, S, M & 1 minute & Touch & Object touched & Permanent until discharged & Fortitude partial & Yes\\
    \(\square\) Life bolt & 1 ray/2 levels draws 1 hp from you to deal 1d12 damage to undead & Nec & V, S & 1 standard action & Medium (100 ft. + 10 ft./level) & Up to ﬁve rays & Instantaneous & None & Yes\\
    \(\square\) Ray of sickness & Subject becomes sickened & Nec & V, S & 1 standard action & Close (25 ft. + 5 ft./2 levels) & Ray & 1 round/level & None & Yes\\
    \(\square\) Ray of weakness & Subject takes –2 on attacks, –10 ft speed & Nec & V, S & 1 standard action & Close (25 ft. + 5 ft./2 levels) & Ray & 1 minute/level & None & Yes\\
    \(\square\) Shroud of undeath & Negative energy shroud makes undead perceive you as undead & Nec & V, S, M & 1 standard action & Personal & You & 10 minutes/level (D) & - & -\\
    \(\square\) Spawn screen & Subject resists being transformed into an undead spawn if slain & Nec & V, S, DF & 1 standard action & Touch & - & 1 hour/level & Will negates (harmless) & Yes (harmless)\\
    \(\square\) Stolen breath & Subject has wind knocked out of it & Nec & V, S, F & 1 standard action & Medium (100 ft. + 10 ft./level) & One living creature that breathes air & Instantaneous; see text & None & Yes\\
    \(\square\) Wracking touch & Deal 1d6 damage +1/level; you also deal sneak attack damage if you have any & Nec & V, S & 1 standard action & Touch & Creature touched & Instantaneous & Fortitude half & Yes\\
  \end{longtable}

  \subsubsection*{Level 3}
  \begin{longtable}[H]{ p{8em} p{15em} p{2em} p{5em} p{6em} p{6em} p{10em} p{6em} p{5em} p{2em} }
    \(\blacksquare\) \textbf{Name} & \textbf{Description} & \textbf{School} & \textbf{Comp} & \textbf{Time} & \textbf{Range} & \textbf{T/E/A} & \textbf{Duration} & \textbf{ST} & \textbf{SR}\\
    \endhead
    \(\square\) Anticipate teleportation & Predict and delay the arrival of creatures teleporting into range by 1 round & Abj & V, S, F & 10 minutes & One willing creature touched & 5-ft./level radius emanation from touched creature & 24 hours & None & No\\
    \(\square\) Antidragon aura & Allies gain bonus to AC and saves against dragons & Abj & V, S, M, DF & 1 standard action & Close (25 ft. + 5 ft./2 levels) & - & 1 minute/level & Will negates (harmless) & Yes (harmless)\\
    \(\square\) Avoid planar effects & Provides temporary protection against overtly damaging planar traits & Abj & V & 1 immediate action & 20 ft. & - & 1 minute/level & None & Yes (harmless)\\
    \(\square\) Earthen grace & Subject takes only nonlethal damage from stone and earth & Abj & V, S, M & 1 standard action & Touch & Living creature touched & 1 minute/level & Will negates (harmless) & Yes (harmless)\\
    \(\square\) Eradicate earth & Deals 1d8 points of damage/level to earth creatures (max 10d8) & Abj & V, S, M & 1 standard action & 40 ft. & 40-ft.-radius burst centered on you & Instantaneous & Fortitude half & Yes\\
    \(\square\) Reverse arrows & As protection from arrows, but negated arrows turn back upon their source & Abj & V, S, F & 1 standard action & Personal & You & 10 minutes/level or until  & - & -\\
    \(\square\) Sign of sealing & Magical sigil protects door or chest, deals 1d4/level damage (max 10d4) if opened & Abj & V, S, M & 1 round & Close (25 ft. + 5 ft./2 levels) & One door, chest, or other opening up to 30 sq. ft./level & Permanent & Reﬂex half; see text & No\\
    \(\square\) Blacklight & Create an area of total darkness & Evo & V, S, M & 1 standard action & Close (25 ft. + 5 ft./2 levels) & A 20-ft.-radius emanation centered on a creature, object, or point in space & 1 round/level (D) & Will negates or none (object) & Yes or no (object)\\
    \(\square\) Capricious zephyr & Gale-force winds push creatures & Evo & V, S & 1 standard action & Medium (100 ft. + 10 ft./level) & 5-ft.-diameter sphere & 1 round/level & None or Reﬂex partial; see text & Yes\\
    \(\square\) Chain missile & Multiple missiles deal 1d4+1 damage each, then strike secondary targets & Evo & V, S & 1 standard action & Long (400 ft. + 40 ft./level) & One creature, plus one  & Instantaneous & None & Yes\\
    \(\square\) Flashburst & Flash of light dazzles and blinds creatures in area & Evo & V, S, M/DF & 1 standard action & Long (400 ft. + 40 ft./level) & 20-ft.-radius burst & Instantaneous; see text & Will partial; see text & Yes\\
    \(\square\) Glowing orb & Creates permanent magical light; you control brightness & Evo & V, S, F & 1 standard action & Touch & Magical, controllable light source & Permanent & None & No\\
    \(\square\) Great thunderclap & Loud noise causes stunning, deafness, and knocks prone in a large area & Evo & V, S, F & 1 standard action & Medium (100 ft. + 10 ft./level) & 20-ft.-radius spread & Instantaneous & See text & No\\
    \(\square\) Hailstones & Frigid globes deal 5d6 cold damage & Evo & V, S, M & 1 standard action & Medium (100 ft. + 10 ft./level) & One frigid globe/5 levels & Instantaneous & None & Yes\\
    \(\square\) Light of venya & You radiate pearly light, which you can expend as 2 bolts that deal 2d6 damage, 4d6 against undead and evil outsiders & Evo & - & - & - & - & - & - & -\\
    \(\square\) Manyjaws & One set of jaws/level attacks enemies for 1d6 damage & Evo & V, S, M & 1 standard action & Medium (100 ft. + 10 ft./level) & One pair of disembodied, ﬂying jaws per caster level (maximum ten pairs) & Concentration, up to 3 rounds & See text & Yes\\
    \(\square\) Rainbow blast & Line deals 1d6 damage of each energy type & Evo & V, S, M & 1 standard action & 120 ft. & 120-ft. line & Instantaneous & Reﬂex half & Yes\\
    \(\square\) Resonating bolt & Sonic energy deals 1d4 damage/level (max 10d4) & Evo & V, S & 1 standard action & 60 ft. & 60-ft. line & Instantaneous & Reﬂex half & Yes\\
    \(\square\) Scintillating sphere & 20-ft-radius burst deals 1d6 electricity/level & Evo & V, S, M & 1 standard action & Long (400 ft. + 40 ft./level) & 20-ft.-radius burst & Instantaneous & Reﬂex half & Yes\\
    \(\square\) Shatterfloor & Deals 1d4 sonic/level plus damages ﬂoor surface & Evo & V, S, F & 1 standard action & Medium (100 ft. + 10 ft./level) & 15-ft.-radius spread & Instantaneous & Reﬂex half & Yes\\
    \(\square\) Sonorous hum & Removes need to concentrate to maintain next spell cast & Evo & V, S & 1 standard action & Personal & You & 1 minute/level (D) & - & -\\
    \(\square\) Sound lance & Sonic energy deals 1d8/level damage & Evo & V, S & 1 standard action & Medium (100 ft. + 10 ft./level) & One creature or object & Instantaneous & Fortitude half & Yes\\
    \(\square\) Wall of light & Creates wall of light, can dazzle creatures & Evo & V, S, M & 1 standard action & Close (25 ft. + 5 ft./2 levels) & A straight wall whose area is  & 1 minute/level (D) & None & Yes; see text\\
    \(\square\) Acid breath & Cone of acid deals 1d6 damage/level (max 10d6) & Conj & V, S, M & 1 standard action & 15 ft. & Cone-shaped burst & Instantaneous & Reﬂex half & Yes\\
    \(\square\) Bands of steel & Metallic bands immobilize or entangle subject for 1 round/level & Conj & V, S, M & 1 standard action & Medium (100 ft. + 10 ft./level) & One Medium or smaller creature & 1 round/level & Reﬂex partial & No\\
    \(\square\) Contagious fog & 20-ft-radius cloud of fog inﬂicts disease & Conj & V, S, M & - & Medium (100 ft. + 10 ft./level) & - & 1 round/level & See text & -\\
    \(\square\) Corpse candle & Ghostly hand and candle sheds light, affects incorporeal creatures & Conj & S, M & 1 standard action & Close (25 ft. + 5 ft./2 levels) & Ghostly hand and candle & 1 minute/level (D); see text & None & No\\
    \(\square\) Mage armor, greater & Gives subject +6 armor bonus & Conj & V, S & - & - & - & - & - & -\\
    \(\square\) Mage armor, mass & As mage armor, but one creature/level & Conj & - & - & Close (25 ft. + 5 ft./2 levels) & - & - & - & -\\
    \(\square\) Nauseating breath & Exhale a cone of nauseating gas & Conj & V, S, M & 1 standard action & 30 ft. & Cone-shaped burst & Instantaneous & Fortitude negates & No\\
    \(\square\) Regal procession & As mount, but you summon several mounts & Conj & - & - & - & One mount/level & - & - & -\\
    \(\square\) Servant horde & Create 2d6 unseen servants +1/level (max +15) & Conj & V, S, M & 1 standard action & Close (25 ft. + 5 ft./2 levels) & Invisible, mindless, shapeless servants & 1 hour/level & None & No\\
    \(\square\) Summon undead iii & Summons undead to ﬁght for you & Conj & - & - & - & One or more summoned  & - & - & -\\
    \(\square\) Vipergout & You spit forth celestial or ﬁendish vipers that attack your foes & Conj & V, S, M & 1 standard action & Close (25 ft. + 5 ft./2 levels) & 1d4+3 summoned creatures & 1 round/level & None & Yes\\
    \(\square\) Air breathing & Subjects can breathe air freely & Tra & S, M/DF & 1 standard action & Touch & Living creatures touched & 2 hours/level; see text & Will negates (harmless) & Yes (harmless)\\
    \(\square\) Amorphous form & Subject becomes puddlelike and can slip through cracks quickly & Tra & S, M & 1 standard action & Touch & Willing corporeal creature touched & 1 minute/level (D) & Will negates (harmless) & Yes (harmless)\\
    \(\square\) Bite of the wererat & You gain the Dexterity and attacks of a wererat & Tra & V, S, M & 1 standard action & Personal & You & 1 round/level & - & -\\
    \(\square\) Deeper darkvision & Subject can see 90 ft in magical darkness & Tra & V, S, M & 1 standard action & Touch & Creature touched & 1 hour/level & Will negates (harmless) & Yes \\
    \(\square\) Demon dirge & Demons are stunned and take 3d6 damage/round for 1d4 rounds & Tra & V, S, DF & 1 standard action & Close (25 ft. + 5 ft./2 levels) & Living creature & 1d6 rounds; see text & None or Fortitude partial; see text & Yes\\
    \(\square\) Devil blight & Damage and stun baatezu; damage other lawful and evil creatures & Tra & V, S, DF & 1 standard action & Close (25 ft. + 5 ft./2 levels) & Living creature & 1d6 rounds & None or Fortitude partial; see text & Yes\\
    \(\square\) Diamondsteel & Metal armor provides damage reduction & Tra & V, S, M & 1 standard action & Touch & Suit of metal armor touched & 1 round/level & Will negates (object) & Yes (object)\\
    \(\square\) Dolorous blow & Weapon’s threat range is doubled and threats are automatically conﬁrmed & Tra & V, S & 1 standard action & Touch & Weapon touched & 1 minute/level & None & No\\
    \(\square\) Dragonskin & You gain a bonus to natural armor plus energy resistance 10 & Tra & S, M & 1 standard action & Personal & You & 10 minutes/level & - & -\\
    \(\square\) False gravity & Travel on a solid surface as if that surface had its own gravity & Tra & V, S, M & 1 standard action & Touch & Creature touched & 1 minute/level & Will negates (harmless) & Yes (harmless)\\
    \(\square\) Giant’s wrath & Pebbles you throw become boulders & Tra & V, S, M & 1 swift action & Personal & - & 1 round/level & None & None\\
    \(\square\) Girallon’s blessing & Subject gains one additional pair of arms & Tra & V, S, M & 1 standard action & Touch & Creature touched & 10 minutes/level & Fortitude negates (harmless) & Yes (harmless)\\
    \(\square\) Hamatula barbs & Subjects grow barbs, which damage foes that attack subject in melee & Tra & V, S, M & 1 standard action & Touch & Creature touched & 10 minutes/level & Fortitude negates (harmless) & Yes (harmless)\\
    \(\square\) Primal form & You change into elemental, gain some abilities & Tra & V, S, DF & 1 standard action & Personal & You & 1 minute/level (D) & - & -\\
    \(\square\) Repair serious damage & Repairs 3d8 damage +1/level (max +15) to any construct & Tra & - & - & - & - & - & - & -\\
    \(\square\) Rust ray & Metal objects take 2d6 damage +1/2 levels & Tra & V, S, M & 1 standard action & Close (25 ft. + 5 ft./2 levels) & Ray & - & - & -\\
    \(\square\) Shadow phase & Subject becomes partially incorporeal & Tra & V, S & 1 standard action & Touch & Creature touched & 1 round/level (D) & Fortitude negates (harmless) & Yes (harmless)\\
    \(\square\) Snake’s swiftness, mass & Allies each immediately make one attack & Tra & - & - & Medium (100 ft. + 10 ft./level) & - & - & - & -\\
    \(\square\) Spell vulnerability & Reduce creature’s spell resistance by 1/caster level (max reduction 15) & Tra & V, S & 1 round & Close (25 ft. + 5 ft./2 levels) & One creature & 1 minute/level & Fortitude negates & No\\
    \(\square\) Spiderskin & Subject gains increasing bonus to natural armor, saves against poison, and Hide checks & Tra & V, S, M/DF & 1 standard action & Touch & Creature touched & 10 minutes/level & Will negates (harmless) & Yes (harmless)\\
    \(\square\) Steeldance & Blades hover around you and attack foes & Tra & V, S, F & 1 standard action & Medium (100 ft. + 10 ft./level) & - & 1 round/level & None & No\\
    \(\square\) Stony grasp & Arm made of soil and rock grapples foes & Tra & - & - & - & Animated stone arm & 1 round/level & - & -\\
    \(\square\) Tremorsense & Grants tremorsense to a range of 30 feet & Tra & V, S, F/DF & 1 standard action & Personal & You & 10 minutes/level (D) & - & -\\
    \(\square\) Weapon of energy & Weapon deals extra energy damage & Tra & V, S & 1 standard action & Touch & One weapon & 1 round/level & Fortitude negates (object, harmless) & Yes (harmless, \\
    \(\square\) Weapon of impact & As keen edge, but aids bludgeoning weapons & Tra & V, S & 1 standard action & Touch & One bludgeoning weapon or  & 10 minutes/level & Fortitude negates (harmless, object) & Yes (harmless, \\
    \(\square\) Analyze portal & Find a nearby portal and discover its properties & Div & V, S, M & 1 minute & 60 ft. & Cone-shaped emanation from you to the extreme of the range & Concentration, up to 1 round/level (D) & See text & No\\
    \(\square\) Circle dance & Indicates direction to known individual & Div & V, S & 1 minute & Personal & You & Instantaneous & - & -\\
    \(\square\) Telepathic bond, lesser & Link with subject within 30 ft for 10 minutes/level & Div & V, S & 1 standard action & 30 ft. & - & 10 minutes/level & None & No\\
    \(\square\) Unluck & Subject remakes all rolls, uses worse result for 1 round/level & Div & V, S, M & 1 standard action & Close (25 ft. + 5 ft./2 levels) & One creature & 1 round/level & Will negates & Yes\\
    \(\square\) Mesmerizing glare & Your gaze fascinates creatures & Ench & S & 1 standard action & Close (25 ft. + 5 ft./2 levels) & - & 1 round/level & Will negates & Yes\\
    \(\square\) Miser’s envy & Subject jealously covets nearby object & Ench & V, S, M & 1 standard action & Close (25 ft. + 5 ft./2 levels) & One living creature & 1 round/level & Will negates & Yes\\
    \(\square\) Ray of dizziness & Subject can take only move or standard actions & Ench & V, S, F & 1 standard action & Medium (100 ft. + 10 ft./level) & Ray & 1 round/level & None & Yes\\
    \(\square\) Suppress breath weapon & Subject can’t use its breath weapon & Ench & V & 1 standard action & Close (25 ft. + 5 ft./2 levels) & One creature that has a breath weapon & 1 minute/level & Will negates & No\\
    \(\square\) Cone of dimness & Subjects believe they are engulfed in magical darkness & Ill & V, S & 1 standard action & 60 ft. & Cone-shaped burst & 1 round/level & Will negates; see text & Yes\\
    \(\square\) Shadow binding & Ribbonlike shadows entangle creatures in 10-ft-radius burst & Ill & V, S, M & 1 standard action & Close (25 ft. + 5 ft./2 levels) & 10-ft.-radius burst & 1 round/level & Will negates & Yes\\
    \(\square\) Shadow cache & You open a small portal to the Plane of Shadow through which you can put an item for later retrieval & Ill & V, S & 1 standard action & Touch & 1-ft.-diameter circle & 1 minute/level (D) & No & No\\
    \(\square\) Spectral weapon & Use quasi-real weapon to make touch attacks & Ill & V, S & 1 swift action & 0 ft. & One shadowy blade & 1 round/level (D) & See text & Yes\\
    \(\square\) Suspended silence & Object becomes programmed to create an area of silence at your command & Ill & V, S, M & 1 standard action & Touch & One object & 24 hours or until discharged, then 6 rounds; see text & None (object) & No (object)\\
    \(\square\) Curse of impending blades, mass & Enemies take –2 penalty to AC & Nec & - & - & - & - & - & - & -\\
    \(\square\) Disrupt undead, greater & As disrupt undead, but 1d8 damage/level & Nec & V, S & 1 standard action & Close (25 ft. + 5 ft./2 levels) & Ray & Instantaneous & None & Yes\\
    \(\square\) Healing touch & Heal subject 1d6/2 levels, but take damage equal to half & Nec & V, S & 1 standard action & Touch & Creature touched & Instantaneous & Will half; see text & Yes \\
    \(\square\) Incorporeal enhancement & Grant bonuses to incorporeal undead & Nec & V, S, M & 1 round & Close (25 ft. + 5 ft./2 levels) & One incorporeal undead/level & 24 hours & None & No\\
    \(\square\) Junglerazer & Fey, vermin, plants, and animals take 1d10 damage/level & Nec & V, S, M & 1 standard action & 120 ft. & 120-ft. line & Instantaneous & Reﬂex half & Yes\\
    \(\square\) Mind poison & Your poisonous touch deals Wis damage & Nec & V, S, M & 1 standard action & Touch & - & - & - & Yes\\
    \(\square\) Skull watch & Skull shrieks when creature enters warded area & Nec & V, S, F & 1 standard action & Touch & One humanoid skull & Permanent & See text & No\\
    \(\square\) Spider poison & Touch deals 1d6 Str damage, repeats in 1 minute & Nec & V, S, M & 1 standard action & Touch & Living creature touched & Instantaneous; see text & Fortitude negates & Yes\\
    \(\square\) Undead lieutenant & Chosen undead can give orders to undead in your control & Nec & V, S & 1 standard action & Close (25 ft. + 5 ft./2 levels) & One undead creature; see text & 24 hours & Will negates (harmless) & Yes (harmless)\\
    \(\square\) Undead torch & Undead creature gains blue aura that gives +2d6 damage against living creatures & Nec & V, S, M & 1 standard action & Close (25 ft. + 5 ft./2 levels) & - & 1 round/level & Will negates (harmless) & Yes (harmless)\\
    \(\square\) Enhance familiar & Your familiar receives +2 bonus on saves, combat rolls, and AC for 1 hour/level & Uni & V, S & 1 standard action & Touch & Familiar touched & 1 hour/level & None & Yes (harmless)\\
    \(\square\) Fortify familiar & Your familiar gains 2d8 temporary hp, +2 to armor, 25\% chance to avoid extra sneak attack and critical hit damage & Uni & V, S & 1 standard action & Touch & Familiar touched & 1 hour/level & None & Yes (harmless)\\
  \end{longtable}

  \subsubsection*{Level 4}
  \begin{longtable}[H]{ p{8em} p{15em} p{2em} p{5em} p{6em} p{6em} p{10em} p{6em} p{5em} p{2em} }
    \(\blacksquare\) \textbf{Name} & \textbf{Description} & \textbf{School} & \textbf{Comp} & \textbf{Time} & \textbf{Range} & \textbf{T/E/A} & \textbf{Duration} & \textbf{ST} & \textbf{SR}\\
    \endhead
    \(\square\) Dispelling screen & Targeted dispel magic on any creatures and unattended items, +10 max on caster level check & Abj & V, S, M & 1 standard action & Close (25 ft. + 5 ft./2 levels) & Energy wall whose area is  & 1 minute/level (D) & None & No\\
    \(\square\) Forceward & Creates a sphere of force that protects against force effects and keeps out incorporeal creatures & Abj & V, S & 1 round & 15 ft. & 15-ft.-radius sphere centered on you & 1 minute/level & Will negates; see text & \\
    \(\square\) Portal alarm, improved & Warded portal alerts you or a creature designated by you to creatures passing through it & Abj & V, S, F & - & - & - & 8 hours/level (D) & - & -\\
    \(\square\) Ray of deanimation & Ray deals 1d6 damage/level to constructs & Abj & V, S & 1 standard action & Close (25 ft. + 5 ft./2 levels) & Ray & - & - & -\\
    \(\square\) Ray deflection & Ray attacks are reﬂected away & Abj & V, S, F & 1 standard action & Personal & You & 1 minute/level & None & No\\
    \(\square\) Resist energy, mass & Creatures ignore damage from speciﬁed energy type & Abj & - & - & Close (25 ft. + 5 ft./2 levels) & - & - & - & -\\
    \(\square\) Resistance, greater & Subject gains +3 on saving throws & Abj & - & - & - & - & 24 hours & - & -\\
    \(\square\) Wall of chaos & Wall blocks creatures of opposite alignment & Abj & - & - & - & - & - & - & -\\
    \(\square\) Wall of evil & Wall blocks creatures of opposite alignment & Abj & - & - & - & - & - & - & -\\
    \(\square\) Wall of good & Wall blocks creatures of opposite alignment & Abj & V, S, M/DF & 1 standard action & Close (25 ft. + 5 ft./2 levels) & A straight wall whose area is  & 10 minutes/level & See text & Yes\\
    \(\square\) Wall of law & Wall blocks creatures of opposite alignment & Abj & - & - & - & - & - & - & -\\
    \(\square\) Blistering radiance & Light dazzles creatures, deals 2d6 ﬁre damage in 50-ft-radius spread & Evo & V, S, M & 1 standard action & Long (400 ft. + 40 ft./level) & 50-ft.-radius spread & 1 round/level & None and Fortitude partial; see text & Yes\\
    \(\square\) Defenestrating sphere & Cloudy gray sphere knocks enemies prone, hurls them upward for subsequent falling damage & Evo & V, S, F & 1 standard action & Medium (100 ft. + 10 ft./level) & 2-ft.-radius sphere & 1 round/level (D) & Fortitude partial; see text & Yes\\
    \(\square\) Dragon breath  &  & Evo & V, S, M/DF & 1 standard action & Personal & You & 1 round/level & - & -\\
    \(\square\) Energy spheres & Five colored spheres attack with or negate acid, cold, electricity, ﬁre, and sonic energy & Evo & V, S, M & 1 standard action & Close (25 ft. + 5 ft./2 levels) & Five ﬂoating spheres & 1 round/level or until discharged & Reﬂex half; see text & Yes; see text\\
    \(\square\) Explosive cascade & Bouncing ﬂame ball deals 1d6/level ﬁre damage & Evo & V, S, M & 1 standard action & Close (25 ft. + 5 ft./2 levels) & One 5-ft. square/level, all of which must be connected in one continuous path (S) & Instantaneous & Reﬂex half & Yes\\
    \(\square\) Floating disk, greater & As ﬂoating disk, but you can ride it & Evo & V, S, M & 1 standard action & Close (25 ft. + 5 ft./2 levels) & 3-ft.-diameter disk of force & 1 hour/level & None & \\
    \(\square\) Force chest & 2-ft-cube chest made of force & Evo & V, S, M & 1 standard action & 0 ft. & Box of force 2 ft. on a side & 24 hours/level (D) & None & No\\
    \(\square\) Force claw & Claw of force guards an area, making opportunity attacks & Evo & V, S, M & 1 standard action & Medium (100 ft. + 10 ft./level) & Invisible claw of force & 1 round/level (D) & None & Yes\\
    \(\square\) Force missiles & Unerring missiles of force strike for 2d6 damage and explode in a burst & Evo & V, S & 1 standard action & Medium (100 ft. + 10 ft./level) & - & Instantaneous & None & Yes\\
    \(\square\) Forcewave & Bull rushes all creatures within 10 ft & Evo & V, S, F & 1 swift action & 10 ft. & 10-ft. burst of force centered on you & Instantaneous & None & Yes\\
    \(\square\) Stone sphere & 3-ft.-diameter stone sphere rolls over your enemies& Evo & V, S, M & 1 standard action & Medium (100 ft. + 10 ft./level) & One 5-ft.-diameter stone sphere & 1 round/level & Reﬂex negates; see text & Yes\\
    \(\square\) Sword of deception & Blade of energy attacks independently, deals 1d4 damage, penalizes subsequent save & Evo & V, S, F & 1 standard action & Medium (100 ft. + 10 ft./level) & Pale green blade of force & 1 round/level (D) & None & Yes\\
    \(\square\) Thunderlance & Lance of force deals 3d6 damage and might dispel force effects & Evo & V, S, M & 1 standard action & 0 ft. & A spearlike beam & 1 round/level (D) & None & No\\
    \(\square\) Vortex of teeth & 3d8 points of damage due to force per round to all creatures in the area & Evo & V, S, M & 1 standard action & Medium (100 ft. + 10 ft./level) & Hollow cylinder (40-ft. radius,  & 1 round/level (D) & None & Yes\\
    \(\square\) Wingbind & A net of force entangles the subject, causing it to fall from the sky & Evo & V, S & 1 standard action & Medium (100 ft. + 10 ft./level) & One creature & 1 round/level (D) & Reﬂex negates & Yes\\
    \(\square\) Blast of flame & 60-ft cone of ﬁre (1d6/level damage) & Conj & V, S, M & 1 standard action & 60 ft. & Cone-shaped burst & Instantaneous & Reﬂex half & No\\
    \(\square\) Bloodstar & Hovering construct does Con damage each time foe is damaged & Conj & V, S, F & 1 standard action & Medium (100 ft. + 10 ft./level) & A bloodstar & 1 round/level & Fortitude negates & Yes\\
    \(\square\) Ethereal mount & You conjure swift mounts on the Ethereal Plane & Conj & - & - & - & One quasi-real mount, plus  & - & - & -\\
    \(\square\) Orb of acid & Ranged touch, 1d6/level acid damage and subject might be sickened & Conj & V, S & 1 standard action & Close (25 ft. + 5 ft./2 levels) & One orb of acid & Instantaneous & Fortitude partial; see text & No\\
    \(\square\) Orb of cold & Ranged touch, 1d6/level cold damage and subject might be blinded & Conj & - & - & - & One orb of cold & - & - & -\\
    \(\square\) Orb of electricity & Ranged touch, 1d6/level electricity damage and subject might be entangled & Conj & - & - & - & One orb of electricity & - & - & -\\
    \(\square\) Orb of fire & Ranged touch, 1d6/level ﬁre damage and subject might be dazed & Conj & - & - & - & One orb of ﬁre & - & - & -\\
    \(\square\) Orb of force & Globe of force deals 1d6/level damage (max 10d6) & Conj & V, S & 1 standard action & Medium (100 ft. + 10 ft./level) & One orb of force & Instantaneous & None & No\\
    \(\square\) Orb of sound & Ranged touch, 1d4/level sonic damage and subject might be deafened & Conj & - & - & - & One orb of sonic energy & - & - & -\\
    \(\square\) Translocation trick & You and subject switch places and appear as each other & Conj & V & 1 standard action & Medium (100 ft. + 10 ft./level) & - & 10 minutes/level & Will negates; see text & Yes\\
    \(\square\) Wall of sand & Swirling sand blocks ranged attacks, slows movement through & Conj & V, S, M/DF & - & Medium (100 ft. + 10 ft./level) & A straight wall whose area is up to one 10-ft. square/level (S) & Concentration + 1 round/level & None & No\\
    \(\square\) Wall of water & Creates shapeable transparent wall of water & Conj & V, S, M & 1 standard action & Medium (100 ft. + 10 ft./level) & A straight wall whose area is up to one 10-ft. square/level (S) & 10 minutes/level & Reﬂex negates; see text & No\\
    \(\square\) Attune form & Grant creature temporary protection against overtly damaging planar traits & Tra & V, S, M/DF & 1 standard action & Touch & One creature/3 levels & 24 hours & None & No\\
    \(\square\) Backlash & Subject takes damage if it uses spells against another creature & Tra & V, S & 1 standard action & Touch & Creature touched & 10 minutes/level or until discharged & Will negates & Yes\\
    \(\square\) Bite of the werewolf & You gain the Strength and attacks of a werewolf & Tra & V, S, M & 1 standard action & Personal & You & 1 round/level & - & -\\
    \(\square\) Blinding breath & Your breath weapon blinds subjects & Tra & - & - & - & - & - & - & -\\
    \(\square\) Corporeal instability & Transform a creature into an amorphous mass & Tra & V, S & 1 standard action & Touch & Living creature touched & 1 round/level (D) & Fortitude negates & Yes\\
    \(\square\) Darkvision, mass & As darkvision, but affects one/level subjects & Tra & - & - & 10 ft. & - & - & - & -\\
    \(\square\) Displacer form & You change into displacer beast, gain some abilities & Tra & V, S, M & 1 standard action & Personal & You & 1 round/level (D) & - & -\\
    \(\square\) Entangling staff & Quarterstaff can grapple and constrict foes & Tra & V, S, F & 1 swift action & Touch & Quarterstaff touched & 1 round/level (D) & Yes (harmless, object) & Yes (harmless)\\
    \(\square\) Fire stride & Teleport from one ﬁre to another & Tra & V, S & 1 standard action & Personal & You & 10 minutes/level or until  & - & -\\
    \(\square\) Flame whips & Your forelimbs deal 6d6 ﬁre damage & Tra & V, S & 1 standard action & Personal & Flaming whips & 1 round/level (D) & - & -\\
    \(\square\) Flight of the dragon & You grow dragon wings & Tra & V, M & 1 standard action & Personal & You & 10 minutes/level (D) & - & -\\
    \(\square\) Metal melt & Melts metal object without heat & Tra & V, S, M & 1 standard action & Close (25 ft. + 5 ft./2 levels) & Nonmagical metal object weighing up to 5 lb./level & 1 round & Will negates (object) & Yes (object)\\
    \(\square\) Perinarch & Gain greater control over Limbo’s morphic essence & Tra & V, S, DF & 1 standard action & Close (25 ft. + 5 ft./2 levels) & - & 1 round/level; see text & None (object) and Reﬂex negates; see text & No\\
    \(\square\) Raise from the deep & Creature or sunken ship made buoyant & Tra & V & 1 minute & Long (400 ft. + 40 ft./level); see text & One creature or object & 1 hour/level & Fortitude negates (object) & Yes (object)\\
    \(\square\) Repair critical damage & Repairs 4d8 damage +1/level (max +20) to any construct & Tra & - & - & - & - & - & - & -\\
    \(\square\) Ruin delver’s fortune & Cast on another creature’s turn and choose one of several beneﬁts & Tra & V & 1 immediate action & Personal & You & 1d4 rounds & - & -\\
    \(\square\) Scramble portal & You randomize the destination of a magic portal & Tra & V, S, M & 1 standard action & Close (25 ft. + 5 ft./2 levels) & One interplanar gate or portal & 1 round/level & None (for portal) & No\\
    \(\square\) Sharptooth & One of your natural weapons deals damage as if you were one size larger & Tra & V, S & 1 standard action & Personal & You & 1 round/level & - & -\\
    \(\square\) Spell enhancer & Lets you cast another spell in the same round at +2 caster level & Tra & V & 1 swift action & Personal & You & 1 round & - & -\\
    \(\square\) Voice of the dragon & +10 on Bluff, Diplomacy, and Intimidate checks; can use one suggestion & Tra & V, S & 1 standard action & Personal & You & 10 minutes/level (D) & - & -\\
    \(\square\) Wings of air, greater & Subject’s ﬂight maneuverability improves by two steps & Tra & - & - & - & - & - & - & -\\
    \(\square\) Assay spell resistance & +10 bonus on caster level checks to defeat one creature’s spell resistance & Div & V, S & 1 swift action & Personal & You & 1 round/level & - & -\\
    \(\square\) Know vulnerabilities & Determine subject’s vulnerabilities and resistances & Div & V, S & 1 standard action & Close (25 ft. + 5 ft./2 levels) & One creature & Instantaneous & Will negates & Yes\\
    \(\square\) Treasure scent & You detect valuable metals and gems & Div & V, S & 1 standard action & Personal & You & 1 hour/level & - & -\\
    \(\square\) Battle hymn & Allies can reroll one Will save/round & Ench & V, S & 1 standard action & 30 ft. & - & 1 round/level & Will negates (harmless) & Yes \\
    \(\square\) Rebuke, greater & Subject cowers for 1d4 rounds & Ench & - & - & - & - & - & - & -\\
    \(\square\) Sensory deprivation & All of subject’s senses are blocked & Ill & V, S, M & 1 standard action & Medium (100 ft. + 10 ft./level) & One creature & 1 round/level & Will disbelief & Yes\\
    \(\square\) Shadow well & Subject enters gloomy pocket plane and emerges frightened & Ill & V, S & 1 standard action & Close (25 ft. + 5 ft./2 levels) & One creature & 1 round/level & Will negates; see text & Yes\\
    \(\square\) Rebuking breath & Your breath weapon rebukes undead & Nec & S & 1 swift action & Personal & Your breath weapon & 1 round & - & -\\
    \(\square\) Iron bones & Corporeal undead gains +6 natural armor bonus & - & - & - & - & - & - & - & -\\
  \end{longtable}

  \subsubsection*{Level 5}
  \begin{longtable}[H]{ p{8em} p{15em} p{2em} p{5em} p{6em} p{6em} p{10em} p{6em} p{5em} p{2em} }
    \(\blacksquare\) \textbf{Name} & \textbf{Description} & \textbf{School} & \textbf{Comp} & \textbf{Time} & \textbf{Range} & \textbf{T/E/A} & \textbf{Duration} & \textbf{ST} & \textbf{SR}\\
    \endhead
    \(\square\) Anticold sphere & Sphere hedges out cold creatures and protects you from cold & Abj & V, S & 1 standard action & 10 ft. & 10-ft.-radius emanation centered on you & 10 minutes/level (D) & None & Yes\\
    \(\square\) Contingent energy resistance & Energy damage triggers a resist energy spell & Abj & V, S, M & 1 minute & - & - & 1 hour/level (D) & - & -\\
    \(\square\) Dispelling breath & Your breath weapon acts as a targeted dispel magic to all creatures in its area & Abj & S & 1 swift action & Personal & Your breath weapon & 1 round & - & -\\
    \(\square\) Duelward & +4 on Spellcraft checks, counterspell as an immediate action & Abj & V, S, M & 1 standard action & Personal & You & 1 round/level or until  & - & -\\
    \(\square\) Indomitability & Subject can’t be reduced below 1 hp & Abj & V, S & 1 standard action & Touch & Creature touched & 1 minute/level or until discharged & None (harmless) & Yes (harmless)\\
    \(\square\) Ironguard, lesser & Subject becomes immune to nonmagical metal & Abj & V, S, M & 1 standard action & Touch & Creature touched & 1 round/level & Will negates (harmless) & Yes (harmless)\\
    \(\square\) Reciprocal gyre & Creature or object takes 1d12 damage/level of spell affecting it (max 25d12) & Abj & V, S, M & 1 standard action & Medium (100 ft. + 10 ft./level) & One creature or object & Instantaneous & Will half, then Fortitude negates; see text & No\\
    \(\square\) Refusal & Spellcasters and creatures with spell-like abilities are prevented from entering an area & Abj & V, S, M & 1 standard action & Medium (100 ft. + 10 ft./level)Ef fect and  & Invisible ward that occupies two 10-ft. squares/level (S) & 1 hour/levelSa ving Throw: Will negates; see text & - & Yes\\
    \(\square\) Symbol of spell loss & Triggered rune absorbs spells yet to be cast & Abj & V, S & 10 minutes & 0 ft.; see text & One symbol & See text & Will negates & No\\
    \(\square\) Wall of dispel magic & Creatures passing through a transparent wall becomes subjects of targeted dispel magic & Abj & V, S, DF & 1 standard action & Close (25 ft. + 5 ft./2 levels) & A straight wall whose area is up to one 10-ft. square/level & 1 minute/level & None & No\\
    \(\square\) Ball lightning & Energy ball deals 1d6/level electricity damage & Evo & V, S, M & 1 standard action & Medium (100 ft. + 10 ft./level) & One lightning ball & 1 round/level & Reﬂex negates & Yes\\
    \(\square\) Cacophonic burst & Noise deals 1d6/level sonic damage to all within area & Evo & V, S & 1 standard action & Long (400 ft. + 40 ft./level) & 20-ft.-radius burst & Instantaneous & Reﬂex half & Yes\\
    \(\square\) Cacophonic shield & Shield 10 ft from you blocks sounds, deals 1d6 sonic damage +1/level, and deafens creatures passing through & Evo & V, S & 1 standard action & 10 ft. & 10-ft.-radius emanation centered on you & 1 minute/level (D) & Fortitude partial & Yes\\
    \(\square\) Cyclonic blast & Deals 1d6 damage/level, knocks down creatures & Evo & V, S, F & 1 standard action & 120 ft. & 120-ft. line & Instantaneous & Reﬂex half & Yes\\
    \(\square\) Fire shield, mass & Creatures attacking allies take damage; allies are protected from ﬁre or cold & Evo & V, S, M & 1 round & Close (25 ft. + 5 ft./2 levels) & - & 1 round/level (D) & Will negates (harmless) & Yes (harmless)\\
    \(\square\) Firebrand & One 5-ft burst/level deals 1d6 ﬁre/level plus burning for 1 round & Evo & V, S, M & 1 standard action & Medium (100 ft. + 10 ft./level) & One 5-ft.-radius burst/level (S) & Instantaneous & Reﬂex half & Yes\\
    \(\square\) Fireburst, greater & Subjects within 15 ft take 1d10/level ﬁre damage & Evo & - & - & - & Burst of ﬁre extending 15 ft.  & - & - & -\\
    \(\square\) Moonbow & Three motes of electricity each deal 1d6/2 levels electricity damage to subjects & Evo & V, S, M & 1 standard action & Medium (100 ft. + 10 ft./level) & 1d4 motes of electricity & Instantaneous or up to 4 rounds; see text & None & Yes\\
    \(\square\) Prismatic ray & Ray of light blinds subject, deals random effect & Evo & V, S & 1 standard action & Medium (100 ft. + 10 ft./level) & Ray & Instantaneous & See text & Yes\\
    \(\square\) Shard storm & Blast deals 3d6 damage to creatures in area & Evo & V, S, M & 1 standard action & Medium (100 ft. + 10 ft./level) & One or more 20-ft.-radius bursts of piercing force & 1 round/level & Reﬂex half & Yes\\
    \(\square\) Shroud of flame & Subject bursts into ﬂames, taking 2d6 ﬁre damage/round & Evo & V, S, M & 1 standard action & Medium (100 ft. + 10 ft./level) & One creature & 1 round/level & None & Yes\\
    \(\square\) Sonic rumble & Cone of sound deals damage & Evo & V, S, F & 1 standard action & 30 ft. & Cone-shaped burst & Concentration, up to 1 round/level & Reﬂex half & Yes\\
    \(\square\) Wall of limbs & Whirling limbs deal 5d6 damage and grab creatures passing through & Evo & V, S & 1 round & Medium (100 ft. + 10 ft./level) & A wall of whirling limbs  & 1 round/level (D) & Reﬂex negates; see text & Yes\\
    \(\square\) Acid sheath & Sheath of acid damages those who attack you, enhances acid spells & Conj & V, S, M, F & 1 standard action & Personal & You & 1 round/level (D) & - & -\\
    \(\square\) Arc of lightning & Line of electricity arcs between two creatures (1d6/level damage) & Conj & V, S, M/DF & 1 standard action & Close (25 ft. + 5 ft./2 levels) & A line between two creatures & Instantaneous & Reﬂex half & No\\
    \(\square\) Call zelekhut & A zelekhut performs one duty for you & Conj & V, S, DF, XP & 10 minutes & Close (25 ft. + 5 ft./2 levels) & One called zelekhut & Instantaneous & None & No\\
    \(\square\) Dimension door, greater & Short-range, multiple-use dimension door & Conj & - & - & Touch & You and touched objects or other touched willing creatures & 1 round/2 levels & - & -\\
    \(\square\) Dragon ally, lesser & Exchange services with a 9 HD dragon & Conj & V, XP & - & - & - & Instantaneous & None & No\\
    \(\square\) Hidden lodge & Creates sturdy cottage camouﬂaged to blend into natural surroundings & Conj & V, S, F; see text & - & - & - & 24 hours & - & -\\
    \(\square\) Phantasmal thief & Creates an unseen force that steals from others & Conj & V, S, M & 1 standard action & Close (25 ft. + 5 ft./2 levels) & One invisible, mindless, shapeless thief & 1 round/level & None & No\\
    \(\square\) Summon undead v & Summons undead to ﬁght for you & Conj & - & - & - & One or more summoned  & - & - & -\\
    \(\square\) Viscid glob & Ranged touch attack hurls 5-ft-diameter glob of glue at subject & Conj & V, S, M & 1 standard action & Medium (100 ft. + 10 ft./level) & One creature & 1 hour/level & Reﬂex negates & Yes\\
    \(\square\) Vitriolic sphere & Potent acid deals 6d6 acid damage plus possible damage in following 2 rounds & Conj & V, S, M & 1 standard action & Long (400 ft. + 40 ft./level) & 10-ft.-radius burst & Instantaneous; see text & Reﬂex partial; see text & No\\
    \(\square\) Bite of the wereboar & You gain the Strength and attacks of a wereboar & Tra & V, S, M & 1 standard action & Personal & You & 1 round/level & - & -\\
    \(\square\) Breath weapon substitution & Your breath weapon deals a different kind of damage than normal & Tra & S & 1 swift action & Personal & Your breath weapon & 1 round & - & -\\
    \(\square\) Draconic might & Gain +5 to Str, Con, Cha; +4 natural armor; immunity to magic sleep and paralysis effects & Tra & V, S & 1 standard action & Touch & Living creature touched & 1 minute/level (D) & Fortitude negates (harmless) & Yes (harmless)\\
    \(\square\) Dragonsight & Gain low-light vision, darkvision, and blindsense & Tra & V, S, F & 1 standard action & Personal & You & 1 hour/level (D) & - & -\\
    \(\square\) Enlarge person, greater & Subject remains enlarged for 1 hour/level & Tra & - & - & Touch & - & 1 hour/level (D) & - & -\\
    \(\square\) Ethereal breath & Your breath weapon manifests on the Ethereal Plane & Tra & S & 1 swift action & Personal & Your breath weapon &  & - & -\\
    \(\square\) Fiendform & Assume form and abilities of ﬁendish creature, demon, or devil & Tra & V, S, M & 1 standard action & Personal & You & 1 minute/level & - & -\\
    \(\square\) Fly, mass & One creature/level ﬂies at speed of 60 ft & Tra & V, S & - & Close (25 ft. + 5 ft./2 levels) & - & - & - & -\\
    \(\square\) Gutsnake & 10-ft. tentacle grows from your stomach and attacks your enemies & Tra & V, S, F & 1 standard action & Personal & You & 1 round/level (D) & - & -\\
    \(\square\) Lucent lance & Ambient light forms lance, deals various damage & Tra & V, S, F & 1 standard action & Close (25 ft. + 5 ft./2 levels) & Ray & Instantaneous & None & Yes; see text\\
    \(\square\) Nightstalker’s transformation & Gain +4 Dex, +3 luck bonus to AC, +5 luck bonus on Ref saves, +3d6 sneak attack, and evasion & Tra & V, S, M & 1 standard action & Personal & You & 1 round/level (D) & - & -\\
    \(\square\) Reduce person, greater & Subject remains reduced for 10 minutes/level & Tra & - & - & - & - & 10 minutes/ & - & -\\
    \(\square\) Spell matrix, lesser & Magical matrix stores a 3rd-level or lower spell to be cast later as quickened spell & Tra & V, S, F & 1 standard action & Personal & Matrix that holds one of your spells & 10 minutes/level (D) & - & -\\
    \(\square\) Stunning breath & Your breath weapon also stuns creatures for 1 round & Tra & S & 1 swift action & Personal & Your breath weapon & Instantaneous & - & -\\
    \(\square\) Surefooted stride, mass & As surefooted stride but multiple subjects & Tra & - & - & Close (25 ft. + 5 ft./2 levels) & One creature/level, no two of  & - & - & -\\
    \(\square\) Vulnerability & Reduces an opponent’s damage reduction & Tra & V, S & 1 standard action & Touch & Creature touched & 1 round/level & Will negates & Yes\\
    \(\square\) Xorn movement & Touched creature swims through earth like a xorn & Tra & V, S, F & 1 standard action & Touch & Creature touched & 1 round/level; see text & Will negates (harmless) & Yes (harmless)\\
    \(\square\) Illusory feast & Subjects become dazed by illusory food & Ill & V, S, M & 1 standard action & Long (400 ft. + 40 ft./level) & 40-ft.-radius spread & 1 round/level & Will negates & Yes\\
    \(\square\) Shadow form & Gain +4 on Hide, Move Silently, and Escape Artist checks, and concealment; you can move through obstacles if you have ranks in Escape Artist & Ill & V, S, M & 1 standard action & Personal & You & 1 minute/level (D) & - & -\\
    \(\square\) Shadow hand & Medium hand blocks opponents or carries items & Ill & V, S & 1 standard action & Close (25 ft. + 5 ft./2 levels) & Medium shadowy hand & 1 round/level (D) & None & Yes\\
    \(\square\) Shadowfade & Opens a portal to the Plane of Shadow & Ill & V, S & 1 standard action & Close (25 ft. + 5 ft./2 levels) & One 10-ft. portal to the Plane of Shadow & 1 minute/level & Will negates & Yes\\
    \(\square\) Death throes & Your body explodes when you die & Nec & V, S & 1 standard action & Personal & You & 1 hour/level or until you are killed & None & No\\
    \(\square\) Graymantle & Inhibits creature’s ability to heal and regenerate for 1 round/level & Nec & V, S, M & 1 standard action & Medium (100 ft. + 10 ft./level) & One living creature & 1 round/level & Fortitude negates & Yes\\
    \(\square\) Miasma of entropy & Rot all natural materials in 30-ft cone-shaped burst & Nec & V, S & 1 standard action & 30 ft. & Cone-shaped burst or one solid object; see text & Instantaneous & Fortitude half or Will negates (object); see text & Yes (object)\\
    \(\square\) Night’s caress & Touched foe takes 1d6 points of damage/level plus 1d6+2 Con damage & Nec & V, S & 1 standard action & Touch & Creature touched & Instantaneous & Fortitude partial; see text & Yes\\
    \(\square\) Spiritwall & Wall of spirit-forms causes panic, deals 1d10 damage if touched, can bestow negative levels if passed through & Nec & V, S, M & 1 standard action & Medium (100 ft. + 10 ft./level) & Swirling wall whose area is  & 1 minute/level (D) & None; see text & No\\
    \(\square\) Wrack & Renders creature helpless with pain & Nec & V, S & 1 standard action & Close (25 ft. + 5 ft./2 levels) & One humanoid & 1 round/level + 3d10 minutes; see text & Fortitude negates & Yes\\
    \(\square\) Planar tolerance & Provides long-term protection against overtly damaging planar traits & - & - & - & - & - & 1 hour/level & - & -\\
  \end{longtable}

  \subsubsection*{Level 6}
  \begin{longtable}[H]{ p{8em} p{15em} p{2em} p{5em} p{6em} p{6em} p{10em} p{6em} p{5em} p{2em} }
    \(\blacksquare\) \textbf{Name} & \textbf{Description} & \textbf{School} & \textbf{Comp} & \textbf{Time} & \textbf{Range} & \textbf{T/E/A} & \textbf{Duration} & \textbf{ST} & \textbf{SR}\\
    \endhead
    \(\square\) Anticipate teleportation, greater & Predict and delay the arrival of creatures teleporting into range by 3 rounds & Abj & - & - & - & - & - & - & -\\
    \(\square\) Aura of evasion & All within 10 ft gain evasion against breath weapons & Abj & V, S, M, DF & 1 standard action & 10 ft. & 10-ft.-radius emanation centered on you & 1 minute/level & No & No\\
    \(\square\) Resistance, superior & Subject gains +6 on saving throws & Abj & - & - & - & - & 24 hours & - & -\\
    \(\square\) Ruby ray of reversal & Ray negates magical or mundane hazards & Abj & V, S, F & 1 standard action & Medium (100 ft. + 10 ft./level) & One natural or magical hazard; see text & Instantaneous & None & No\\
    \(\square\) Seal portal & Seal an interplanar portal or gate & Abj & V, S, M & 1 standard action & Close (25 ft. + 5 ft./2 levels) & One interplanar gate or portal & Permanent (D) & None & No\\
    \(\square\) Sign of sealing, greater & Magical sigil protects door, chest, or open space, deals 1d6/level damage (max 20d6) if opened & Abj & - & 10 minutes & - & One door, chest,  & - & - & -\\
    \(\square\) Transcribe symbol & Safely moves an untriggered magical symbol to another location & Abj & V, S, F & 1 standard action & Touch & Magic symbol touched & 10 minutes or until discharged & None & No\\
    \(\square\) Fires of purity & Subject bursts into magical ﬂame, becoming a dangerous weapon & Evo & V, S, DF & 1 standard action & Touch & Creature touched & 1 round/level & See text & Yes (harmless); \\
    \(\square\) Howling chain & Chain of force trips and attacks opponents & Evo & V, S, F & 1 standard action & Medium (100 ft. + 10 ft./level) & One chain of force & 1 round/level & See text & Yes\\
    \(\square\) Ray of light & Ray blinds subject & Evo & V, S & 1 standard action & Close (25 ft. + 5 ft./2 levels) & Ray & Instantaneous & None & Yes\\
    \(\square\) Acid storm & Deals 1d6/level acid damage (max 15d6) in a 20-ft radius & Conj & V, S, M & 1 standard action & Medium (100 ft. + 10 ft./level) & Cylinder (20-ft. radius, 20 ft. high) & Instantaneous & Reﬂex half & No\\
    \(\square\) Fire spiders & Swarm of Fine ﬁre elementals deals ﬁre damage in an area & Conj & V, S, M & 1 standard action & Close (25 ft. + 5 ft./2 levels) & Fiery spiders that cover a 10-ft.-radius spread & 1 round/level & Reﬂex half & Yes\\
    \(\square\) Gemjump & Teleport to the location of a specially prepared gem & Conj & V, S, F & 1 round & Unlimited; see text & You and willing creatures totaling up to one/3 levels; see text & Until triggered & None; see text & No; see text\\
    \(\square\) Tunnel swallow & Tunnel’s peristaltic convulsions deal 1d6 points of damage/level (max 15d6) & Conj & V, S, M & 1 standard action & Medium (100 ft. + 10 ft./level) & Tunnel section up to 20 ft. in diameter and up to 50 ft. long & Instantaneous & Reﬂex partial; see text & No\\
    \(\square\) Wall of gears & Creates wall of moving gears that deals 1d6 damage/2 levels to creatures within 10 ft & Conj & V, S, M & 1 standard action & Medium (100 ft. + 10 ft./level) & A straight wall of moving gears whose area is up to one 10-ft. square/level; see text & 1 minute/level & See text & No\\
    \(\square\) Bite of the weretiger & You gain the Strength and attacks of a weretiger & Tra & V, S, M & 1 standard action & Personal & You & 1 round/level & - & -\\
    \(\square\) Brilliant blade & Weapon or projectiles shed light, ignore armor & Tra & V, S & 1 standard action & Close (25 ft. + 5 ft./2 levels) & One melee or thrown  & 1 minute/level & Will negates (harmless, object) & Yes \\
    \(\square\) Cloak of the sea & Gain blur, freedom of movement, and water breathing while in water & Tra & V, S, DF & 1 standard action & Touch & Creature touched & 1 hour/level (D) & Will negates (harmless) & Yes (harmless)\\
    \(\square\) Extract water elemental & Pulls water from victim, forms water elemental & Tra & V, S & 1 standard action & Close (25 ft. + 5 ft./level) & One living creature & Instantaneous & Fortitude half & Yes\\
    \(\square\) Hardening & Increases object’s hardness by 1 point/2 levels & Tra & V, S, M & 1 standard action & Touch & One item of a volume no greater than 10 cu. ft./level; see text & Permanent & None & Yes (object)\\
    \(\square\) Make manifest & You cause a creature on a coexistent plane to appear on your plane & Tra & V, S & 1 standard action & Close (25 ft. + 5 ft./2 levels) & One creature & 1 round/level & Will negates & Yes\\
    \(\square\) Ooze puppet & You telekinetically control an ooze & Tra & V, S & 1 standard action & Medium (100 ft. + 10 ft./level) & One ooze & 24 hours/level & Fortitude negates & Yes\\
    \(\square\) Stone body & Your body becomes living stone & Tra & V, S, M & 1 standard action & Personal & You & 1 minute/level (D) & - & -\\
    \(\square\) Subvert planar essence & Reduces subject’s damage reduction and spell resistance & Tra & V, S, M/DF & 1 standard action & Medium (100 ft. + 10 ft./level) & 20-ft.-radius emanation centered on a point in space & 1 round/level & Fortitude negates & Yes\\
    \(\square\) Interplanar telepathic bond & Link lets allies communicate across planes & Div & V, S, M & 1 standard action & Close (25 ft. + 5 ft./2 levels) & - & 10 minutes/level (D) & None & No\\
    \(\square\) Probe thoughts & Read subject’s memories, one question/round & Div & V, S & 1 minute & Close (25 ft. + 5 ft./2 levels) & One living creature & Concentration, up to 1 round/level & Will negates; see text & Yes\\
    \(\square\) Dream casting & Alter subject’s dreams to produce desired effect & Ill & - & 1 hour & - & You and one dreamer & 24 hours/level; see text & Will negates; see text & -\\
    \(\square\) Illusory pit & Creatures in area are knocked prone while believing they’re falling & Ill & V, S & 1 round & Medium (100 ft. + 10 ft./level) & 10-ft. cube/level & Concentration + 1 round/level & Will disbelief & No\\
    \(\square\) Reflective disguise, mass & Viewers see subjects as their own species and gender & Ill & - & - & Close (25 ft. + 5 ft./2 levels) & - & 12 hours (D) & Will negates & Yes\\
    \(\square\) Shadowy grappler & Illusory force grapples subject & Ill & V, S, M & - & Medium (100 ft. + 10 ft./level) & One creature & 1 round/level (D) & Will partial; see text & Yes\\
    \(\square\) Aura of terror & You gain an aura of fear, or your frightful presence becomes more effective & Nec & V & 1 standard action & 30-ft.-radius emanation centered on you & - & 1 minute/level & Will negates; see text & Yes\\
    \(\square\) Contagion, mass & As contagion, but 20-ft radius & Nec & - & - & Medium (100 ft. + 10 ft./level) & 20-ft.-radius spread & - & - & -\\
    \(\square\) Fleshshiver & Subject is stunned for 1 round, takes 1d6/level damage, and is nauseated for 1d4+2 rounds & Nec & V, S, M & 1 standard action & Close (25 ft. + 5 ft./2 levels) & One living creature & Instantaneous & Fortitude partial; see text & Yes\\
    \(\square\) Ghoul gauntlet & Convert victim to a ghoul under your control & Nec & V, S & 1 standard action & Touch & One living humanoid creature & Instantaneous & Fortitude negates & Yes\\
    \(\square\) Imperious glare & You cause subjects to cower in fear & Nec & S & 1 standard action & Close (25 ft. + 5 ft./2 levels) & - & 1 round/level & Will negates; see text & Yes\\
    \(\square\) Incorporeal nova & Destroy incorporeal undead & Nec & V, S & 1 standard action & Medium (100 ft. + 10 ft./level) & 50-ft.-radius burst & Instantaneous & Will negates & Yes\\
    \(\square\) Opalescent glare & Kill creatures with a look, or make them very afraid & Nec & V, S, DF & 1 standard action & Personal & You & Instantaneous & Will partial; see text & Yes\\
    \(\square\) Ray of entropy & Subject takes –4 Strength, Dexterity, and Constitution & Nec & V, S & 1 standard action & Close (25 ft. + 5 ft./2 levels) & Ray & 1 minute/level & None & Yes\\
    \(\square\) Revive undead & Restores undeath to undead that was destroyed up to 1 day/level ago & Nec & V, S, M & 1 minute & Touch & Destroyed undead creature touched & Instantaneous & None & No\\
    \(\square\) Spectral touch & Your touch bestows one negative level/round & Nec & V, S & 1 standard action & Touch & - & 1 round/level (D); see text & Fortitude negates & Yes\\
    \(\square\) Imbue familiar with spell ability & You transfer spells and casting ability into your familiar & Uni & V, S & 1 standard action & Touch & Familiar touched & 1 hour/level & Will negates (harmless) & Yes (harmless)\\
  \end{longtable}

  \subsubsection*{Level 7}
  \begin{longtable}[H]{ p{8em} p{15em} p{2em} p{5em} p{6em} p{6em} p{10em} p{6em} p{5em} p{2em} }
    \(\blacksquare\) \textbf{Name} & \textbf{Description} & \textbf{School} & \textbf{Comp} & \textbf{Time} & \textbf{Range} & \textbf{T/E/A} & \textbf{Duration} & \textbf{ST} & \textbf{SR}\\
    \endhead
    \(\square\) Antimagic ray & Subject loses all magical powers & Abj & V, S, M & 1 standard action & Close (25 ft. + 5 ft./2 levels) & Ray & 1 round/level & Will negates (object) & Yes\\
    \(\square\) Dispelling screen, greater & Targeted dispel magic on any creatures and unattended items, +20 max on caster level check & Abj & - & - & - & - & - & - & -\\
    \(\square\) Energy immunity & Subject and equipment gain immunity to damage of speciﬁed energy type & Abj & V, S & 1 standard action & Touch & Creature touched & 24 hours & None & Yes (harmless)\\
    \(\square\) Ghost trap & Incorporeal creatures turn corporeal & Abj & V, S & 1 standard action & 5 ft./level & 5 ft./level-radius emanation centered on you & 1 minute/level (D) & None & No\\
    \(\square\) Hide from dragons & Dragons can’t perceive one subject/2 levels & Abj & S, M & 1 standard action & Touch & - & 10 minutes/level (D) & Will negates (harmless) & Yes (harmless)\\
    \(\square\) Ironguard & Subject becomes immune to all metal & Abj & V, S, F, M & - & - & - & - & - & -\\
    \(\square\) Emerald flame fist & Touch attack deals 3d6 + ﬁre damage 1/level (max +20); subject can be engulfed by ﬂame for additional damage & Evo & V, S & 1 standard action & Touch & Creature or object touched & 1 round/level; see text & See text & Yes\\
    \(\square\) Ice claw & Claw of ice grapples and deals cold damage & Evo & V, S, F & 1 standard action & Medium (100 ft. + 10 ft./level) & 10-ft. ice claw & 1 round/level (D) & None & Yes\\
    \(\square\) Prismatic eye & Orb produces individual prismatic rays as touch attacks & Evo & V, S, F & 1 standard action & Medium (100 ft. + 10 ft./level) & Magical eye & 1 round/level & See text & Yes\\
    \(\square\) Radiant assault & 1d6 damage/level, victims dazed or dazzled & Evo & V, S, F & 1 standard action & Long (400 ft. + 40 ft./level) & 20-ft.- radius burst & Instantaneous & Will partial & Yes\\
    \(\square\) Submerge ship & You control ship mentally while it travels underwater & Evo & V, S, F & 10 minutes & Touch & Ship touched & 1 hour/level & None & No\\
    \(\square\) Call kolyarut & A kolyarut performs one duty for you & Conj & V, S, DF, XP & 10 minutes & Close (25 ft. + 5 ft./2 levels) & One called kolyarut & Instantaneous & None & No\\
    \(\square\) Dragon ally & As lesser dragon ally, but up to 15 HD & Conj & - & - & - & One called dragon of 18 HD  & - & - & -\\
    \(\square\) Stun ray & Subject stunned 1d4+1 rounds & Conj & V, S, M & 1 standard action & Close (25 ft. + 5 ft./2 levels) & Ray & 1d4+1 rounds; see text & Fortitude partial; see text & Yes\\
    \(\square\) Animate breath & Your breath weapon becomes an elemental & Tra & S & 1 standard action & Personal & Your breath weapon & 1 round/level & - & -\\
    \(\square\) Bite of the werebear & You gain the Strength and attacks of a werebear & Tra & V, S, M & 1 standard action & Personal & You & 1 round/level & - & -\\
    \(\square\) Body of war & You change into warforged titan, gain some abilities & Tra & V, S, M & 1 standard action & Personal & You & 1 round/level (D) & - & -\\
    \(\square\) Brilliant aura & Allies’ weapons become brilliant energy, ignoring armor & Tra & - & - & - & - & 1 round/level & Will negates (harmless) & Yes (harmless)\\
    \(\square\) Elemental body & You take on the qualities of a type of elemental & Tra & V, S, M & 1 standard action & Personal & You & 1 hour/level & - & -\\
    \(\square\) Energy transformation field & Area absorbs magic energy to power a predetermined spell & Tra & V, S, M, XP & 4 rounds & Close (25 ft. + 5 ft./2 levels) & 40-ft.-radius spread & Permanent & None & Yes\\
    \(\square\) Glass strike & Turns subject into glass & Tra & V, S, F & 1 standard action & Close (25 ft. + 5 ft./2 levels) & One creature or 4 cubic ft. of material & 1 hour/level & Fortitude negates & Yes\\
    \(\square\) Spell matrix & Stores up to two spells of 3rd level or lower to be released later & Tra & - & - & - & Matrix that holds two of your  & - & - & -\\
    \(\square\) Stone shape, greater & Sculpts 10 cu & Tra & - & - & - & Stone or stone objects  & - & - & -\\
    \(\square\) Synostodweomer & Channel a spell into positive energy to cure 1d8/spell level & Tra & V, S & 1 swift action & Personal & One of your spells & 1 round & - & -\\
    \(\square\) Hiss of sleep & You induce comatose slumber in subjects & Ench & V & 1 round & Close (25 ft. + 5 ft./2 levels) & - & 1 round/level & Will negates & No\\
    \(\square\) Rebuke, final & As rebuke, except the subject must save or die & Ench & - & - & - & - & - & Will partial & -\\
    \(\square\) Symphonic nightmare & Discordant noise haunts subject’s sleep & Ench & V, S, F & 1 standard action & Touch; see text & Living creature touched; see text & 24 hours/level (D) & Will negates & Yes\\
    \(\square\) Transfix & Humanoids freeze in place until condition you specify is met & Ench & V, S, M & 1 round & Medium (100 ft. + 10 ft./level) & 10-ft.-radius emanation centered on a point in space & 1 hour/level & Will negates; see text & Yes\\
    \(\square\) Solipsism & Subject believes it alone exists & Ill & V & 1 standard action & Medium (100 ft. + 10 ft./level) & One creature & 1 round/level (D) & Will negates & Yes\\
    \(\square\) Arrow of bone & Missile or thrown weapon gains +4 bonus, subject takes 3d6 damage +1/level (max +20) or is slain & Nec & V, S, M & 10 minutes & Touch & One projectile or thrown weapon touched & 1 hour/level or until discharged & Fortitude partial & Yes\\
    \(\square\) Avasculate & Reduce foe to half hp and stun & Nec & V, S & 1 standard action & Close (25 ft. + 5 ft./2 levels) & Ray & Instantaneous & Fortitude partial & Yes\\
    \(\square\) Awaken undead & Grant sentience to otherwise mindless undead & Nec & V, S, M, XP & 1 standard action & Close (25 ft. + 5 ft./2 levels) & - & Instantaneous & None (harmless) & Yes (harmless)\\
    \(\square\) Barghest’s feast & Destroy corpse, potentially preventing its return to life & Nec & V, S, M & 1 round & Touch & Corpse touched & Instantaneous & Will negates (object) & Yes (object)\\
    \(\square\) Energy ebb & Give subject one negative level/round for 1 round/level & Nec & V, S & 1 standard action & Close (25 ft. + 5 ft./2 levels) & Ray & 1 round/level & Fortitude partial; see text & Yes\\
    \(\square\) Evil glare & Paralyze creatures with your glare & Nec & V, S, DF & 1 standard action & 30 feet & Living creatures & 1 round/level; see text & Will negates & Yes\\
    \(\square\) Kiss of the vampire & You gain vampirelike supernatural abilities, but are vulnerable to attacks that harm undead & Nec & V, S, M & 1 standard action & Personal & You & 1 round/level & - & -\\
    \(\square\) Sword of darkness & Blade of negative energy bestows one or more negative levels & Nec & V, S, M & - & - & Black blade of negative  & - & - & -\\
  \end{longtable}

  \subsubsection*{Level 8}
  \begin{longtable}[H]{ p{8em} p{15em} p{2em} p{5em} p{6em} p{6em} p{10em} p{6em} p{5em} p{2em} }
    \(\blacksquare\) \textbf{Name} & \textbf{Description} & \textbf{School} & \textbf{Comp} & \textbf{Time} & \textbf{Range} & \textbf{T/E/A} & \textbf{Duration} & \textbf{ST} & \textbf{SR}\\
    \endhead
    \(\square\) Wall of greater dispel magic & Creatures passing through a transparent wall become subjects of targeted greater dispel magic & Abj & - & - & - & - & - & - & -\\
    \(\square\) Field of icy razors & Creatures in area take normal and cold damage, might be slowed & Evo & V, S, F & 1 standard action & Medium (100 ft. + 10 ft./level) & - & Instantaneous plus 1 round/level; see text & Reﬂex partial & Yes\\
    \(\square\) Lightning ring & Ring of lightning gives you resistance to electricity 20, damages adjacent creatures, and emits two lightning bolts per round & Evo & V, S, M & 1 round & Personal & Ring of electricity & 1 round/2 levels & See text & Yes\\
    \(\square\) Fierce pride of the beastlands & Summon celestial lions and celestial dire lions to follow your commands & Conj & V, S & 10 minutes & Medium (100 ft. + 10 ft./level) & Two or more summoned creatures, no two of which are more than 30 ft. apart & 10 minutes/level (D) & None & No\\
    \(\square\) Plane shift, greater & Plane shift accurately to your desired destination & Conj & - & - & - & - & - & - & -\\
    \(\square\) Excavate & Creates a permanent passage in earth and walls & Tra & V, S, M & 1 standard action & Close (25 ft. + 5 ft./2 levels) & One 5-ft.-by-5-ft. opening, 1 ft./level deep & Instantaneous & None & No\\
    \(\square\) Flensing & Pain and trauma deal 2d6 damage, 1d6 Con damage, 1d6 Cha damage for up to 4 rounds & Tra & V, S, M & 1 standard action & Close (25 ft. + 5 ft./2 levels) & One corporeal creature & 4 rounds & Fortitude partial; see text & Yes\\
    \(\square\) Ghostform & You assume incorporeal form and gain some incorporeal traits and bonuses & Tra & V, S & 1 standard action & Personal & You & 1 round/level (D) & - & -\\
    \(\square\) Make manifest, mass & As make manifest but affecting all creatures in the area & Tra & V, S, M & - & - & 25-ft.-radius emanation centered on a point in space & - & None & -\\
    \(\square\) Stunning breath, greater & Your breath weapon also stuns creatures for 2d4 rounds & Tra & - & - & - & - & - & - & -\\
    \(\square\) Maddening whispers & You induce confusion and madness in subjects & Ench & V & 1 round & Close (25 ft. + 5 ft./2 levels) & - & 1 round/level & Will negates & Yes\\
    \(\square\) Wrathful castigation & Subject dies or is dazed and –4 on saves for 1 round/level & Ench & V, S, F & 1 standard action & Close (25 ft. + 5 ft./2 levels) & One living creature & 1 round/level (D) & See text & Yes\\
    \(\square\) Invisibility, superior & Subject is invisible to sight, hearing, and scent for 1 minute/level, and can attack & Ill & V, S & 1 standard action & Personal or touch & You or a creature or object weighing no more than 100 lb./level & 1 minute/level (D) & Will negates (harmless) & No\\
    \(\square\) Shifting paths & Illusion hides path, creates false new path & Ill & V, S & 10 minutes & Medium (100 ft. + 10 ft./level) & 1-mile radius + 1 mile/level & 1 hour/level & Will disbelief (if interacted with) & Yes\\
    \(\square\) Avascular mass & Reduce foe to half hp and stun, entangle in 20-ft radius from victim & Nec & V, S & 1 standard action & Close (25 ft. + 5 ft./2 levels) & Ray & See text & Fortitude partial and Reﬂex negates; see text & Yes\\
    \(\square\) Bestow curse, greater & As bestow curse, but more severe penalties & Nec & V, S & 1 standard action & Touch & Creature touched & Permanent & Will negates & Yes\\
    \(\square\) Blackfire & Subject is engulfed in black ﬂame, takes 1d4 Con damage and becomes nauseated; ﬂames and effects can spread to adjacent living creatures & Nec & V, S, M & 1 standard action & Medium (100 ft. + 10 ft./level) & Ray & 1 round/level & Fortitude partial and Reﬂex negates; see text & Yes\\
    \(\square\) Heart of stone &  & Nec & V, S, F, XP & 1 hour & Personal & You & 1 year & - & -\\
    \(\square\) Skeletal guard & Create one skeleton/level with turn resistance & Nec & V, S, M & 1 standard action & Touch & One or more ﬁngerbones & Instantaneous & None & No\\
    \(\square\) Veil of undeath & You gain undead traits & Nec & V, S, M & 1 standard action & Personal & You & 10 minutes/level & - & -\\
  \end{longtable}

  \subsubsection*{Level 9}
  \begin{longtable}[H]{ p{8em} p{15em} p{2em} p{5em} p{6em} p{6em} p{10em} p{6em} p{5em} p{2em} }
    \(\blacksquare\) \textbf{Name} & \textbf{Description} & \textbf{School} & \textbf{Comp} & \textbf{Time} & \textbf{Range} & \textbf{T/E/A} & \textbf{Duration} & \textbf{ST} & \textbf{SR}\\
    \endhead
    \(\square\) Absorption & You absorb spell energy to power spells of your own & Abj & V, S & 1 standard action & Personal & You & Until expended or 10  & - & -\\
    \(\square\) Effulgent epuration & Creates one sphere/level to negate hostile magic & Abj & V, S & 1 standard action & Close (25 ft. + 5 ft./2 levels) & One magic-absorbing sphere per caster level & 1 round/level & Will negates (harmless) & Yes (harmless)\\
    \(\square\) Magic miasma & Solid fog reduces caster level by –4 & Abj & V, S, M & 1 standard action & Medium (100 ft. + 10 ft./level) & 30-ft.-radius emanation centered on a point in space & 1 round/level & None; see text & No\\
    \(\square\) Maw of chaos & Chaotic energy dazes, deals damage, impedes concentration & Abj & V, S, M & 1 standard action & Medium (100 ft. + 10 ft./level) & 15-ft.-radius emanation centered on a point in space & 1 round/level & Will partial & Yes\\
    \(\square\) Reaving dispel & On a targeted dispel, steal spell power and effects for yourself & Abj & - & - & - & - & - & See text & No\\
    \(\square\) Unbinding & Frees everyone in range from spells that constrain or bind & Abj & V, S, M, DF & 1 round & 180 ft. & 180-ft.-radius burst centered on you & Instantaneous & None & No\\
    \(\square\) Instant refuge & Transport to a safe location of your choice & Evo & V, S, M, XP & 10 minutes & Personal & You & Until discharged & - & -\\
    \(\square\) Reality maelstrom & Hole in reality sends creatures and objects to another plane & Evo & V, S, M & 1 standard action & Medium (100 ft. + 10 ft./level) & 20-ft.-radius emanation  & 1 round & Will negates, Reﬂex negates; see text & Yes\\
    \(\square\) Abyssal army & Summons demons to ﬁght for you & Conj & V, S & 10 minutes & Medium (100 ft. + 10 ft./level) & Two or more summoned creatures, no two of which are more than 30 ft. apart & 10 minutes/level (D) & None & No\\
    \(\square\) Black blade of disaster & Floating magic weapon disintegrates subjects & Conj & V, S & 1 standard action & Close (25 ft. + 5 ft./2 levels) & Sword-shaped planar rift & Concentration, up to 1 round/level & None & Yes\\
    \(\square\) Call marut & A marut performs one duty for you & Conj & V, S, DF, XP & 10 minutes & Close (25 ft. + 5 ft./2 levels) & One called marut & Instantaneous & None & No\\
    \(\square\) Dragon ally, greater & As lesser dragon ally, but up to 21 HD & Conj & - & - & - & One called  & - & - & -\\
    \(\square\) Heavenly host & Summons archons to ﬁght for you & Conj & V, S & 10 minutes & Medium (100 ft. + 10 ft./level) & Two or more summoned creatures, no two of which are more than 30 ft. apart & 10 minutes/level (D) & None & No\\
    \(\square\) Hellish horde & Summons devils to ﬁght for you & Conj & V, S & 10 minutes & Medium (100 ft. + 10 ft./level) & Two or more summoned creatures, no two of which are more than 30 ft. apart & 10 minutes/level (D) & None & No\\
    \(\square\) Obedient avalanche & Snowy avalanche crushes and buries your foes & Conj & V, S & 1 standard action & Medium (100 ft. + 10 ft./level) & 20-ft.-radius avalanche of snow centered on a point in space; see text & Instantaneous & Reﬂex half or Reﬂex negates; see text & No\\
    \(\square\) Sphere of ultimate destruction & Featureless black sphere does 2d6/level damage, disintegrates & Conj & V, S, M & 1 standard action & Medium (100 ft. + 10 ft./level) & 2-ft.-radius sphere & 1 round/level (D) & Fortitude partial; see text & Yes\\
    \(\square\) Summon elemental monolith & Calls powerful elemental creature to ﬁght for you & Conj & V, S, M & 1 round & Medium (100 ft. + 10 ft./level) & One summoned elemental monolith & Concentration, up to 1 round/level & None & No\\
    \(\square\) Awaken construct & Construct gains humanlike sentience & Tra & V, S, M, XP & 8 hours & Touch & One construct & Instantaneous & Will negates (harmless) & Yes (harmless)\\
    \(\square\) Breath weapon admixture & Add a second kind of energy to your breath weapon & Tra & S & 1 swift action & Personal & Your breath weapon & 1 round & - & -\\
    \(\square\) Replicate casting & Duplicate observed spell or spell-like ability & Tra & V, S & 1 round; see text & See text & One spell or spell-like ability & See text & See text & See text\\
    \(\square\) Spell matrix, greater & Stores up to three spells of 3rd level or lower to be released later & Tra & - & - & - & Matrix that holds three of  & - & - & -\\
    \(\square\) Transmute rock to lava & Transforms one 10-ft cube with subsequent fire damage and effects & Tra & V, S & 1 standard action & Medium (100 ft. + 10 ft./level) & One 10-ft. cube & Instantaneous & Reﬂex half; see text & No\\
    \(\square\) Undermaster & You gain earth-related spell-like abilities & Tra & V, M & 1 standard action & Personal & You & 5 rounds & - & -\\
    \(\square\) Eye of power & As arcane eye, but you can cast spells of 3rd level or lower through it & Div & V, S, M & 10 minutes & Unlimited & Magical sensor & 1 minute/level (D) & None & No\\
    \(\square\) Hindsight & You see into the past & Div & V, S, M & 1 hour & 60 ft. & 60-ft.-radius emanation centered on you & Instantaneous & None & No\\
    \(\square\) Programmed amnesia & Destroy, alter, or replace memories in subject creature & Ench & V, S, M & 10 minutes & Close (25 ft. + 5 ft./2 levels) & One living creature & Permanent & Will negates & Yes\\
    \(\square\) Enervating breath & Your breath weapon also bestows 2d4 negative levels & Nec & S & 1 swift action & Personal & Your breath weapon & 1 round & - & -\\
    \(\square\) Plague of undead & Animates horde of undead & Nec & V, S, M & 1 standard action & Close (25 ft. + 5 ft./2 levels) & - & Instantaneous & None & No\\
  \end{longtable}
\end{center}
\end{document}
